---
title: "Alternative Strategies"
author: "Kelly Mistry"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(reshape2)
library(ggplot2)
library(dplyr)
library(here)
library(tictoc)
library(fdrtool)
library(jagsUI)
library(scales)
library(vctrs)
library(doParallel)
library(jagsUI)

source(here("Scripts/00_user_inputs.R"))
source(here("Scripts/01_model_functions.R"))
source(here("Scripts/02_results_functions.R"))
source(here("estimation_model_functions.R"))

##### Shared parameters 
# Target area
area_size <- 50
# Carrying capacity
K <- 60*area_size
# Growth probability (p_g)
g_density_prob <- 0.75 
# Number of days in a quarter
day_time_step <- 91

# MCMC settings for estimation model (use the same for all)
nt <- 1
nb <- 10000 # 20000 
ni <- 30000 + nb # 50000
nc <- 3

# test

```

```{r jags_model_code}

# JAGS Removal Estimation Model - simple growth with zero inflation
sink("removal_model_alt_strategies.jags")
cat("
model {

# Set up first row of N
for(k in 1:S) {
  p.miss[1,k,1:N_prior] <- rep(1/N_prior,N_prior)
  miss[1,k] ~ dcat(p.miss[1,k,1:N_prior])
  N[k,1,1] <-  N.base[k,1,1] + miss[1,k]
}

# Parameter priors

# Encounter probability intercept and slope for each method
for(k in 1:S) {
  for(j in 1:J) {
      beta.p[k, j] ~ dunif(0, 10)
      alpha.p[k, j] ~ dunif(-10, 10)
    for(day in method_days[j,]) {
      beta.p[k, day] <- beta.p[k, j]
      alpha.p[k, day] <- alpha.p[k, j]
    }
  }
}


# Growth per size class priors
r1 ~ dgamma(1,0.3) # growth for small size class
r2 ~ dgamma(1,0.3) # growth for medium size class
r3 ~ dgamma(1,0.3) # growth for large size class
r4 ~ dgamma(1,0.3) # growth for xlarge size class

# Zero-inflation prior
# with different variables for each size class
# for(k in 1:S) {
#   psi[k] ~ dunif(0, 1)
# }
# with two variables, one for small snakes and the other for the 3 upper size classes
psi[1] ~ dunif(0,1)
psi[2] ~ dunif(0,1)
psi[3] <- psi[2]
psi[4] <- psi[2]

# Transition matrix (used for population size class growth between primary sampling periods)
for(t in 1:(Q-1)){
  P[1,t] <- r1^days_btwn[t]
  P[2,t] <- r2^days_btwn[t]
  P[3,t] <- r3^days_btwn[t]
  P[4,t] <- r4^days_btwn[t]
}


for(t in 1:Q) { # start primary sampling period loop  
  for(k in 1:S) { # start size class loop
      for(i in 1:I) { # start secondary sampling instances loop
      # Calculate encounter probability for each method, secondary sampling instance and primary sampling period
      # Odd columns are visual, even columns are trap
        logit(p[k,i,t]) <- alpha.p[k,i] + beta.p[k,i] * log(xi[i,t])
      # Calculate removals based on encounter probability and M (population in within i instance)
        Y[k,i,t] ~ dbin(p[k,i,t],N[k,i,t])
      # Calculate N using last time step N minus summed removals
        N[k,i+1,t] <- N[k,i,t] - Y[k,i,t]
      } # end secondary sampling instances loop
  # Calculate remaining population at the end of the primary sampling period
    R[k,t] <- N[k,I,t] - Y[k,I,t]
  } # end size class loop
} # end primary sampling period loop

for (t in 1:(Q-1)) { # start operations between primary sampling period loop
  for(k in 1:S) {
    # Zero-inflation step
    z[k, t] ~ dbern(psi[k])
    # Calculate population at beginning of primary sampling period using remaining population from the end of previous sampling period X transition matrix
    D[k,t] ~ dpois((R[k,t]*P[k,t])*z[k, t] + 0.00001)
  # }
  # # Set up first sampling instance of next primary sampling period
  # for(k in 1:S){ # start size class loop
    N[k,1,t+1] <- D[k,t]
  } # end size class loop
} # end between primary sampling period loop

for(t in 1:Q) { #start primary sampling period loop
  # Summing all size classes into a single N for each primary sampling period
  N.sum[t] <- sum(N[,1,t])
} # end primary sampling period loop

} # end model
", fill= TRUE)
sink()
```

# Alternative management strategies

Common elements of all strategies:

-   All scenarios will be evaluated on probability of reaching each of these objectives (in the simulated population, not estimated):

    -   Full eradication (0 snake/ha)

    -   Reach and maintain 1 snake/ha total density 

    -   Reach and maintain 1 snake/ha combined density for upper 3 size classes

-   50 ha area

    -   Assume rectangle with 220 m width; transects spaced 20 m apart, meaning total coverage would require \~113 transects

-   There could be a range of spatial coverage for transect-based methods, to simulate areas where transects are not possible (25%, 50%, 75%, 100%) - this could be a feature of all scenarios (except the one that is ADS only)

-   10 years maximum (could be less based on thresholds for some strategies)

-   Introduced uncertainty for initial total population and initial size distribution

    -   100 replicates for each combination

#### Starting population permutations:

In Phase I, Staci had 4 permutations of starting populations, with 2 different population sizes and 2 different size distributions. There was low population (\~11 snakes/ha) and normal population (\~22 snakes/ha), and more small snakes (42% of population \< 850 mm SVL) or more extra large snakes (42% of population \>= 1,150 mm SVL). I could do the same, although I'd prefer to have some more population levels. Maybe these:

-   Population levels: low (11 snakes/ha), medium (22 snakes/ha) and high (50 snakes/ha - this is what I've been using).

-   Size distributions: more small (42% small, 19.3% for the other 3), more extra large (42% extra large, 19.3% of the other three). Maybe just start with those two, and if I have time to do more model runs, I can do some more:

    -   Fewer extra large (10% extra large, 30% in the other three), more small and medium (35% small and medium snakes, 15% large and extra large), and more large and extra-large (15% small and medium, 35% large and extra large)

These permutations will have 100 replicates each with the same randomly selected values for the starting populations (and then there will be 100 run of each of those).

```{r starting_pop_permutations}

# Three different mean starting densities
starting_density <- c("low" = 11, "medium" = 22, "high" = 44)
starting_pop <- list()

set.seed(818) # To keep the starting values consistent
for(i in names(starting_density)) {
  starting_pop[[i]] <- round(rnorm(100, starting_density[i]*area_size, 
                             starting_density[i]*area_size*0.1))
}

# Two starting size distributions (could add more if there's time to run them)
starting_size_dist <- list()
starting_size_dist$more_small <- c(0.42, rep((1-0.42)/3,3))
starting_size_dist$more_xlarge <- c(rep((1-0.42)/3,3), 0.42)


```

### Alternative strategies:

1.  Suppression focus with no monitoring

    -   Explores how the population performs when no monitoring is possible, for whatever reason. This is also the current approach being used in parts of Guam.

    -   ADS low effort (1 treatment with 2 drops per quarter)

    -   No thresholds, because no monitoring is occurring so there's nothing to respond to

    -   Population is never estimated (again, no monitoring data)

2.  Experimental approach with many thresholds

    -   Similar to original HMU experiment in the starting point methods, with a lot of thresholds that might cause methods to be changed - this seems more likely to occur during an experiment, and less likely in a purely management scenario, where keeping methods more consistent through time might be more desirable.

    -   The population is estimated as frequently as possible, every 2 quarters.

    -   Starting methods: ADS: low effort (1 treatment) per quarter; Visual survey: medium effort (6 weeks, 2 teams) per quarter; Trap: medium effort (6 weeks) per quarter; Bait tubes: medium effort (6 weeks) per quarter

    -   Threshold 1: estimated mean density is of upper size classes is 3 snake/ha combined

        -   If met: in next 2 quarters, stop ADS, traps & bait tubes and double number of visual survey teams (5 weeks, 4 teams)

    -   Threshold 2: estimated mean small size class density is increasing by \>=10%

        -   If met: in next 2 quarters, double number of visual survey teams (5 weeks, 4 teams)

    -   Threshold 3: estimated mean density of entire population is =\< 0 snakes/ha for at least 2 quarters

        -   If met: stop all methods for 1 quarter, do 1 round of visual survey (5 weeks, 2 teams) in 2nd quarter.

3.  Eradication focus without ADS

    -   A strategy with no ADS but a high amount of transect-based effort, geared towards eradication with relatively little monitoring, as ADS is a little precarious and could disappear (company that provides the materials is not entirely solvent, it sounds like). The only threshold is also geared towards eradication, but only on one size class to see if that would be sufficient to signal if the reproductively active part of the population is nearing or reaching eradication (as opposed to making the threshold based on the entire population).

    -   Starting methods: Visual survey: high effort (9 weeks, 2 teams) per quarter; Trap: high effort (9 weeks) per quarter; Bait tubes: high effort (9 weeks) per quarter. 3 weeks of each quarter is only visual & trap, no bait tubes, to allow for monitoring

    -   Threshold 1: estimated mean density of extra-large size class is 0 for \>=2 quarters

        -   If met: stop all methods for 2 quarters, do 1 round of low effort visual survey (2 weeks, 4 teams) in 4th quarter

    -   Estimate population every 4 quarters

4.  TBD

5.  TBD

### Strategy 1: Suppression focus without monitoring

-   One treatment (2 drops) per quarter over entire area

-   Run for 10 years

-   I don't think it matters when in the quarter it happens - I'll just put it in the middle

```{r strategy_1_setup}

### Manually set IBM parameters
# Target area in ha
#area_size <- 50 
# Carrying capacity
#K <- 60*area_size
# Initial total N 
#N <- 50*area_size
# Initial size distribution
#size_dist <- c(0.4, 0.1, 0.1, 0.4)
# Growth probability (p_g)
#g_density_prob <- 0.75 
# Number of quarters to generate - 10 years
erad_quarter_time_step <- 4*10
#day_time_step <- 91

# Quarters where eradication methods are used, and which days in that quarter:
erad_quarters <- list()
erad_quarters$ADS <- c(1:erad_quarter_time_step)
erad_days <- list()
for(quarter in 1:erad_quarter_time_step) {
  erad_days[[quarter]] <- list()
  erad_days[[quarter]]$ADS <- c(45, 48)
}
names(erad_days) <- paste0("quarter_", erad_quarters$ADS)

# Bounds of primary sampling period (since there is no monitoring, this doesn't matter but it's a required parameter for a function)
primary_sampling_period <- c(0,0)

# Coverage for each method in a quarter 
erad_coverage <- list()
erad_coverage$ADS <- 1
# Transect coverage and overlap of ADS over transects - there aren't actually any transect methods so neither of these is relevant, but they are required parameters at the moment and its not a high priority to fix that, so keeping them in for now
erad_coverage$transects_per_quarter <- 0
ADS_overlap_on_transect <- 1 

# Another required parameter that doesn't matter for this strategy, because there is no visual survey occurring
num_teams <- list()
num_teams$visual <- 0
```

```{r strategy_1_run_once}

# Running model 
erad_quarter_results <- quarter_operations(initial_N = 11*area_size, 
                                           initial_size_dist = c(0.4, 0.1, 0.1, 0.4), 
                                           p_g = g_density_prob,
                                           lambda = lambda,
                                           total_quarters = erad_quarter_time_step,
                                           total_days = day_time_step,
                                           erad = "on",
                                           erad_method = names(erad_quarters),
                                           erad_coverage = erad_coverage,
                                           primary_sampling_period = primary_sampling_period,
                                           erad_quarters = erad_quarters,
                                           erad_days = erad_days,
                                           type_of_run = "initial")

# Plotting the total population in each quarter
erad_plot_1 <- ggplot(erad_quarter_results$all_quarters, 
                      aes(x = Quarter, fill = size_category)) +
  geom_bar() +
  geom_hline(yintercept = K) +
  theme_bw() +
  scale_x_continuous(breaks = unique(erad_quarter_results$all_quarters$Quarter), labels = unique(erad_quarter_results$all_quarters$Quarter))
```

Block to run the IBM model for all permutations:

```{r strategy_1_replicates}

# Number of replicates for each starting pop permutation
num_replicates <- 100


for(P in 1:length(starting_density)) { # Starting pop permutation (low, medium or high)
  # Timin the biggest loops
  ptm <- proc.time()
  N_reps <- starting_pop[[P]]
  for(D in 1:length(starting_size_dist)) { # Starting size distribution permutation (more small or more large)
    size_dist <- starting_size_dist[[D]]
    for(variant in 7:length(N_reps)) { # Start running through the 100 starting pop variants for the selected permutation
      replicates_strategy_one <- list()
      N <- N_reps[variant]
      for(n in 1:num_replicates) {
          # Running model 
         replicates_strategy_one[[n]] <- quarter_operations(initial_N = N, 
                                                   initial_size_dist = size_dist, 
                                                   p_g = g_density_prob,
                                                   lambda = lambda,
                                                   total_quarters = erad_quarter_time_step,
                                                   total_days = day_time_step,
                                                   erad = "on",
                                                   erad_method = names(erad_quarters),
                                                   erad_coverage = erad_coverage,
                                                 primary_sampling_period = primary_sampling_period,
                                                 erad_quarters = erad_quarters,
                                                 erad_days = erad_days,
                                                 ADS_overlap_on_transect = ADS_overlap_on_transect,
                               type_of_run = "initial",
                               num_teams = num_teams)
         print(paste0("replicate ", n, " complete"))
      } # End of replicates loop
      # Save each variant list
      saveRDS(replicates_strategy_one, file = here("Results", "alt_strategies", paste0("strategy_one_IBM_start_pop_",names(starting_pop)[P], "-", names(starting_size_dist)[D], "-var_", variant, ".rds")))
      print(paste0("variant ", variant, " complete"))
    } # End of variants loop
    print(paste0("size_dist ", D, " complete"))
  } # End of size distribution permutation loop
  # Stop the clock
  proc.time() - ptm
  print(paste0("starting pop ", P, " complete"))
} # End of starting pop permutation loop
      




# Reading results back in
replicates_strategy_one <- readRDS(file = here("Results", "alt_strategies", paste0("strategy_one_IBM_start_pop_low-more_small-var_1.rds")))
  
### Reformat IBM results for plotting
erad_plot_data_1 <- list()
for(n in 1:num_replicates) {
  erad_plot_data_1[[n]] <- list()
  results <- replicates_strategy_one[[n]]$all_quarters
  for(quarter in 1:erad_quarter_time_step) {
    erad_plot_data_1[[n]][[quarter]] <- as.data.frame(matrix(NA, nrow = 4, ncol = 2))
    colnames(erad_plot_data_1[[n]][[quarter]]) <- c("size_category", "N")
    for(size in 1:length(size_class_names)) {
      erad_plot_data_1[[n]][[quarter]][size, 1] <- size_class_names[size]
      erad_plot_data_1[[n]][[quarter]][size, 2] <- nrow(results[results$Quarter == (quarter+1) & results$size_category == size_class_names[size],])
    }
  }
  names(erad_plot_data_1[[n]]) <- c(1:erad_quarter_time_step)
}
names(erad_plot_data_1) <- paste0("replicate", c(1:num_replicates))  

erad_plot_data_melted_1 <- melt(erad_plot_data_1, id.vars = colnames(erad_plot_data_1[[1]][[1]]))
colnames(erad_plot_data_melted_1)[c(3:4)] <- c("Quarter", "variant")
erad_plot_data_melted_1$size_category <- factor(erad_plot_data_melted_1$size_category, levels = size_class_names)

# erad_plot_data_melted_1$variant <- factor(erad_plot_data_melted_1$variant, levels = paste0("variant_", c(1:num_variants)))

variants_plot_1 <- ggplot(erad_plot_data_melted_1, aes(x = as.numeric(Quarter), y = N, color = variant)) +
  geom_path(aes(group = variant), show.legend = FALSE) +
  geom_point(show.legend = FALSE) +
  #geom_hline(yintercept = K) +
  facet_wrap(vars(size_category)) +
  theme_bw()

```

Parallel processing version

```{r strategy_1_parallel}

# For low population, more small
P <- 1
D <- 2

N_reps <- starting_pop[[P]]
size_dist <- starting_size_dist[[D]]

library(doParallel)
# Detect the number of clusters available
n_cores <- detectCores()
# Select half of them
cl <- makeCluster(n_cores/2)
registerDoParallel(cl)

# Running model variants in parallel
results <- foreach(variant = 1:10, .combine = list)  %dopar% {
  # Calling libraries needed (couldn't figure out how to attach them properly)
  library(reshape2)
  library(ggplot2)
  library(dplyr)
  library(here)
  library(tictoc)
  library(fdrtool)
  library(jagsUI)
  library(scales)
  library(vctrs)
  
  replicates_strategy_one <- list()
  N <- N_reps[variant]
  for(n in 1:num_replicates) {
      # Running model 
     replicates_strategy_one[[n]] <- quarter_operations(initial_N = N, 
                                               initial_size_dist = size_dist, 
                                               p_g = g_density_prob,
                                               lambda = lambda,
                                               total_quarters = erad_quarter_time_step,
                                               total_days = day_time_step,
                                               erad = "on",
                                               erad_method = names(erad_quarters),
                                               erad_coverage = erad_coverage,
                                             primary_sampling_period = primary_sampling_period,
                                             erad_quarters = erad_quarters,
                                             erad_days = erad_days,
                                             ADS_overlap_on_transect = ADS_overlap_on_transect,
                           type_of_run = "initial",
                           num_teams = num_teams)
     print(paste0("replicate ", n, " complete"))
  } # End of replicates loop
  # Save each variant list
  saveRDS(replicates_strategy_one, file = here("Results", "alt_strategies", "Strategy_one", paste0("strategy_one_IBM_start_pop_",names(starting_pop)[P], "-", names(starting_size_dist)[D], "-var_", variant, ".rds")))
  #print(paste0("variant ", variant, " complete"))
  replicates_strategy_one
}


# Stop the cluster
stopCluster(cl = cl)
```

### Strategy 2: Experimental approach (medium to high effort with all methods, using many thresholds)

-   Run for maximum of 10 years

-   The population is estimated every 2 quarters, and evaluated to see if any thresholds are met or exceeded. If not, initial methods continue

-   Initial methods: ADS: low effort (1 treatment) per quarter; Visual survey: medium effort (6 weeks, 2 teams) per quarter; Trap: medium effort (6 weeks) per quarter; Bait tubes: medium effort (6 weeks) per quarter

-   Thresholds:

    -   Estimated mean density is of upper size classes is \<= 3 snake/ha combined

        -   If met: in next 2 quarters, stop ADS, traps & bait tubes and double number of visual survey teams to cover twice the area (6 weeks, 4 teams)

    -   Estimated mean small size class density is increasing by \>=10%

        -   If met: in next 2 quarters, double number of visual survey teams to cover twice the area (6 weeks, 4 teams), keeping other methods the same as initial

    -   Estimated mean density of entire population is =\< 0 snakes/ha for at least 2 quarters

        -   If met: stop all methods for 1 quarter, then do medium effort visual survey (6 weeks with 2 teams, at the beginning of the quarter) for the next quarter to estimate the population (only works because data exists from previous quarters - a single primary sampling period isn't enough on its own)

-   Transect details:

    -   There are assumed to be 113 transects

    -   I assume that one team can do a visual survey OR check traps on 4 transects in 1 night, and one team can check bait tubes on 8 transects in 1 night

        -   This means that one team could survey or check traps on all transects in 29 days, or two teams could do it 15 days

    -   Visual surveys occur every other day for 6 weeks (20 days)

        -   This means that 2 teams are required to cover the entire area each quarter (some overlap could occur, but that wouldn't change the coverage parameter since 100% coverage is the maximum)

            -   Going with 100% coverage with two teams for now

    -   Traps are checked every 3rd day for the same 6 weeks (14 days)

        -   Two teams could cover the whole area (with 1 night requiring checking 5 transects), or one team could cover 50% of the area each quarter

            -   Going with 100% coverage with two teams for now (because I don't have method-specific spatial selection set up, although I could do that)

    -   Bait tubes are checked every 3rd day for 6 weeks (different 6 weeks than the visual survey and trapping; 14 days)

        -   Bait tubes are faster to check, so one team can check the entire area in each quarter

```{r strategy_2_define_thresholds}


#mean_N_df <- est_v_sim_N_plots$mean_N_df

strat_2_threshold_fun <- function(mean_N_df,
                                  upper_3_threshold = 3,
                                  total_threshold = 0.01,
                                  small_increase_threshold = 0.1,
                                  area = area_size,
                                  size_class = size_class_names) {
  # Condition (default is initial)
  condition <- "initial"
  # Adding a column with density
  mean_N_df$mean_density <- mean_N_df$N/area
  # Identifying final time step (and the one right before)
  last_quarters <- tail(sort(unique(mean_N_df$Quarter)),2)
  # Separating final time step
  last_quarter_means <- mean_N_df[mean_N_df$Quarter == last_quarters[2], ]
  
  ## Calculating mean densities 
  # Upper 3 size classes combined
  upper_3_mean_density <- sum(last_quarter_means$N[last_quarter_means$size_class != size_class[1]])/area
  # Total population
  total_mean_density <- sum(last_quarter_means$N)
  
  # Calculating density increase between second to last and last time step for small snakes
  small_increase <- mean_N_df$mean_density[mean_N_df$size_class == size_class[1] & mean_N_df$Quarter == last_quarters[2]]/mean_N_df$mean_density[mean_N_df$size_class == size_class[1] & mean_N_df$Quarter == last_quarters[1]] - 1
  
  
  ## Threshold 1: Estimated mean density is of upper size classes is <= 3 snake/ha combined but total population is greater than > 0.01
  if(upper_3_mean_density <= upper_3_threshold & total_mean_density > total_threshold) {
    condition <- "threshold_1"
  }  
    
  ## Threshold 2: Estimated mean small size class density is increasing by >=10% compared to previous time step
  if (upper_3_mean_density >= upper_3_threshold & total_mean_density > total_threshold & small_increase >= small_increase_threshold) {
    condition <- "threshold_2"
  }
  
  ## Threshold 3: Estimated mean density of entire population is =< 0.01 snakes/ha for at least 2 quarters
  if(total_mean_density <= total_threshold) {
    condition <- "threshold_3"
  }
  
  return(condition)
}

```

```{r strategy_2_setup}

### Manually set IBM parameters
# Number of quarters to generate - 10 years
erad_quarter_time_step <- 2

# Methods for all evenatualities; starting, threshold 1, threshold 2 and threshold 3
method_option_names <- c("initial", paste0("threshold_", c(1:3)))
method_options <- list()
for(option in 1:length(method_option_names)) {
  method_options[[option]] <- list()
}
names(method_options) <- method_option_names

# Identifying the methods that will be used under each of these conditions
method_options$initial$methods <- erad_methods
method_options$threshold_1$methods <- erad_methods[2]
method_options$threshold_2$methods <- erad_methods
method_options$threshold_3$methods <- erad_methods[2]

## Quarters where eradication methods are used for each condition
# All methods used in all quarters for first 3 conditions
for(option in 1:3) {
  method_options[[option]]$erad_quarters <- list()
  for(method in method_options[[option]]$methods) {
    method_options[[option]]$erad_quarters[[method]] <- c(1:erad_quarter_time_step)
  }
}
# Condition 4 only has methods occurring in 2nd quarter
method_options$threshold_3$erad_quarters <- 2

## Days where eradication methods are used for each condition
# Initial condition days
method_options$initial$erad_days <- list()
for(quarter in 1:erad_quarter_time_step) {
  method_options$initial$erad_days[[quarter]] <- list()
  # ADS: low effort (1 treatment) per quarter
  method_options$initial$erad_days[[quarter]]$ADS <- c(45, 48)
  # Visual survey: medium effort (6 weeks, 2 teams) per quarter - surveying every other day
  method_options$initial$erad_days[[quarter]]$visual <- seq(2, (7*6 - 1), 2)
  # Trap: medium effort (6 weeks) per quarter - checking traps every 3 days
  method_options$initial$erad_days[[quarter]]$trap <- seq(2, (7*6 - 1), 3)
  # Bait tubes: medium effort (6 weeks) per quarter
  method_options$initial$erad_days[[quarter]]$bait_tube <- seq(7*6, (7*12 - 1), 3)
}
names(method_options$initial$erad_days) <- paste0("quarter_", c(1:erad_quarter_time_step))

# Threshold 1 days (visual surveys only)
method_options$threshold_1$erad_days <- list()
for(quarter in 1:erad_quarter_time_step) {
  method_options$threshold_1$erad_days[[quarter]] <- list()
  # Visual survey: medium effort (6 weeks, 2 teams) per quarter - surveying every other day
  method_options$threshold_1$erad_days[[quarter]]$visual <- seq(2, (7*6 - 1), 2)
}
names(method_options$threshold_1$erad_days) <- paste0("quarter_", c(1:erad_quarter_time_step))

# Threshold 2 days (same as initial - coverage is what expands)
method_options$threshold_2$erad_days <- method_options$initial$erad_days

# Threshold 3 days (no effort in first quarter, with visual effort in the 2nd quarter)
method_options$threshold_3$erad_days <- list()
for(quarter in 1:erad_quarter_time_step) {
  method_options$threshold_3$erad_days[[quarter]] <- list()
  method_options$threshold_1$erad_days[[quarter]]$visual <- seq(2, (7*6 - 1), 2)
}
names(method_options$threshold_3$erad_days) <- paste0("quarter_", c(1:erad_quarter_time_step))



# Bounds of primary sampling periods for each condition (the same for the first 3)
for(option in 1:length(method_options)) {
  method_options[[option]]$primary_sampling_period <- c(2,(7*6 - 1))
}



## Coverage for each method in a quarter for each condition
for(option in 1:length(method_options)) {
  method_options[[option]]$erad_coverage <- list()
  # overlap of ADS over transects (100%) is the same for all conditions
  method_options[[option]]$ADS_overlap_on_transect <- 1 
}
# Initial condition coverage
method_options$initial$erad_coverage$ADS <- 1
# Transect coverage (~50%)
method_options$initial$erad_coverage$transects_per_quarter <- 0.5

# Threshold 1 condition coverage
method_options$threshold_1$erad_coverage$ADS <- 0 # necessary for a function, can fix this later
# Transect coverage (100% because effort is doubled) 
method_options$threshold_1$erad_coverage$transects_per_quarter <- 1

# Threshold 2 condition coverage
method_options$threshold_2$erad_coverage$ADS <- 1
# Transect coverage (100%)
method_options$threshold_2$erad_coverage$transects_per_quarter <- 1

# Threshold 3 condition coverage
method_options$threshold_3$erad_coverage$ADS <- 0 # necessary for a function,
# Transect coverage (~50%)
method_options$threshold_3$erad_coverage$transects_per_quarter <- 0.5

# Number of visual survey teams for each method
for(option in 1:length(method_options)) {
  method_options[[option]]$num_teams <- list()
}

method_options$initial$num_teams$visual <- 1
method_options$threshold_1$num_teams$visual <- 1
method_options$threshold_2$num_teams$visual <- 1
method_options$threshold_3$num_teams$visual <- 1

```

```{r strategy_2_run_IBM_once}

# Initial total N 
N <- 10*area_size
# Initial size distribution
size_dist <- c(0.4, 0.1, 0.1, 0.4)

# Separating out condition 
methods <- method_options$initial$methods
coverage <- method_options$initial$erad_coverage
primary_sampling_period <- method_options$initial$primary_sampling_period
erad_quarters <- method_options$initial$erad_quarters
erad_days <- method_options$initial$erad_days
ADS_overlap <- method_options$initial$ADS_overlap_on_transect
num_teams <- method_options$initial$num_teams

# Running IBM model with initial conditions
erad_quarter_results <- quarter_operations(initial_N = N, 
                                           initial_size_dist = size_dist, 
                                           p_g = g_density_prob,
                                           lambda = lambda,
                                           total_quarters = erad_quarter_time_step,
                                           total_days = day_time_step,
                                           erad = "on",
                                           erad_method =  methods,
                                           erad_coverage = coverage,
                                           primary_sampling_period = primary_sampling_period,
                                           erad_quarters = erad_quarters,
                                           erad_days = erad_days,
                                           ADS_overlap_on_transect = ADS_overlap,
                                           type_of_run = "initial",
                                           num_teams = num_teams)

# Plotting the total population in each quarter
erad_plot_1 <- ggplot(erad_quarter_results$all_quarters, 
                      aes(x = Quarter, fill = size_category)) +
  geom_bar() +
  geom_hline(yintercept = K) +
  theme_bw() +
  scale_x_continuous(breaks = unique(erad_quarter_results$all_quarters$Quarter), labels = unique(erad_quarter_results$all_quarters$Quarter))

```

```{r strategy_2_run_estimation_once}

### Running estimation model once 

# Transforming multiple IBM runs into one dataset 

# Estimation model set up
estimation_inputs <- estimation_inputs_fun(erad_quarter_results$all_observed,
                                           erad_quarter_results$all_effort)

# Call JAGS Function
output_jags <- jags(data = estimation_inputs$data, 
                    inits = estimation_inputs$inits, 
                    parameters.to.save = estimation_inputs$parameters, 
                    "removal_model_simple_zero-inf.jags", 
                    n.chains = nc, 
                    n.thin = nt, 
                    n.iter = ni,
                    n.burnin = nb)

saveRDS(output_jags, file = here("Results", "alt_strategies", "Strategy_two", "Estimation",
"output_jags_test.RDS"))

# Parameter trace plots
traceplot(output_jags, parameters = "alpha.p")
traceplot(output_jags, parameters = "beta.p")
traceplot(output_jags, parameters = c("r1", "r2", "r3", "r4"))
traceplot(output_jags, parameters = "p")
traceplot(output_jags, parameters = "psi")

# Mean N estimates vs simulated real N
est_v_sim_N_plots <- estimated_N_plots(jags_output = output_jags,
                                       erad_quarter_results = erad_quarter_results,
                                       observed_erad_quarters = obs_quarters)

## Testing to see if any thresholds are met
condition <- strat_2_threshold_fun(est_v_sim_N_plots$mean_N_df)



```

```{r strategy_2_run_IBM_again}
last_quarter <- max(mean_N_df$Quarter)
# Get new starting N and starting size distribution from estimation model results
N <- round(sum(mean_N_df$N[mean_N_df$Quarter == last_quarter]))
size_dist <- vector()
for(i in 1:length(size_class_names)) {
  size_dist[i] <- c(mean_N_df$N[mean_N_df$size_class == size_class_names[i] & mean_N_df$Quarter == last_quarter]/N)
}

# Select methods based on condition from estimation model
new_methods <- method_options[[condition]]

# Separating out condition 
methods <- new_methods$methods
coverage <- new_methods$erad_coverage
primary_sampling_period <- new_methods$primary_sampling_period
erad_quarters <- new_methods$erad_quarters
erad_days <- new_methods$erad_days
ADS_overlap <- new_methods$ADS_overlap_on_transect

# Running IBM model with initial conditions
erad_quarter_results <- quarter_operations(initial_N = N, 
                                           initial_size_dist = size_dist, 
                                           p_g = g_density_prob,
                                           lambda = lambda,
                                           total_quarters = erad_quarter_time_step,
                                           total_days = day_time_step,
                                           erad = "on",
                                           erad_method =  methods,
                                           erad_coverage = coverage,
                                           primary_sampling_period = primary_sampling_period,
                                           erad_quarters = erad_quarters,
                                           erad_days = erad_days,
                                           ADS_overlap_on_transect = ADS_overlap)

# Plotting the total population in each quarter
erad_plot_1 <- ggplot(erad_quarter_results$all_quarters, 
                      aes(x = Quarter, fill = size_category)) +
  geom_bar() +
  geom_hline(yintercept = K) +
  theme_bw() +
  scale_x_continuous(breaks = unique(erad_quarter_results$all_quarters$Quarter), labels = unique(erad_quarter_results$all_quarters$Quarter))

```

```{r strategy_2_dynamic_attempt}

# The longest the simulation will go on (10 years for real, 1 to start)
final_time_step <- 4

# List to save IBM results outside of loop
IBM_results <- list()
IBM_observed_results <- list()
IBM_effort_results <- list()
IBM_all_quarters <- as.data.frame(matrix(nrow = 0, ncol = 8))
colnames(IBM_all_quarters) <- c("ID", "sex", "repro_prob", "growth_quant", "variable", "SVL", "Quarter", "size_category")
# Record of effort details as condition changes
estimation_effort_record <- list()
estimation_effort_record$condition <- vector()
estimation_effort_record$primary_sampling_period <- list()
estimation_effort_record$erad_quarters <- list()
estimation_effort_record$erad_days <- list()
# Starting condition
condition <- "initial"
# Starting counter
t <- 1
while(t <= final_time_step) {
  if(t == 1) { # First time step 
    # Initial total N 
    N <- 11*area_size
    # Initial size distribution
    size_dist <- c(0.4, 0.1, 0.1, 0.4)
    # Separating out methods for initial condition
    new_methods <- method_options$initial
    # Setting parameter to run IBM initially
    run_type <- "initial"
    # Creating empty variable so function will run 
    last_quarter_df <- NULL
  } else {
    # Identifying methods condition 
    new_methods <- method_options[[condition]]
    # Isolating population from final time step to make the new initial population
    last_quarter_df <- IBM_results[[t-1]]$quarter_timeseries[[erad_quarter_time_step+1]]
    # Setting parameter to run IBM with existing population
    run_type <- "continuing"
  } 
  # Separating out parameters based on condition 
    methods <- new_methods$methods
    coverage <- new_methods$erad_coverage
    primary_sampling_period <- new_methods$primary_sampling_period
    erad_quarters <- new_methods$erad_quarters
    erad_days <- new_methods$erad_days
    ADS_overlap <- new_methods$ADS_overlap_on_transect
    num_teams <- new_methods$num_teams
    
    # Save method options 
    # Recording condition effort for next estimation round
  estimation_effort_record$condition[t] <- condition
  estimation_effort_record$primary_sampling_period[[t]] <- primary_sampling_period
  estimation_effort_record$erad_quarters[[t]] <- erad_quarters
  estimation_effort_record$erad_days[[t]] <- erad_days
    
    # Running IBM model with condition methods
    IBM_results[[t]] <- quarter_operations(initial_N = N, 
                                           initial_size_dist = size_dist, 
                                           p_g = g_density_prob,
                                           lambda = lambda,
                                           total_quarters = erad_quarter_time_step,
                                           total_days = day_time_step,
                                           erad = "on",
                                           erad_method =  methods,
                                           erad_coverage = coverage,
                                           primary_sampling_period = primary_sampling_period,
                                           erad_quarters = erad_quarters,
                                           erad_days = erad_days,
                                           ADS_overlap_on_transect = ADS_overlap,
                                           type_of_run = run_type,
                                           last_quarter_df = last_quarter_df,
                                           num_teams = num_teams)
  
    # Save IBM results from this run
      saveRDS(IBM_results, file = here("Results", "alt_strategies", "Strategy_two", "IBM", paste0("IBM_results_test_IBM_set-", t, ".rds")))
    
  # Saving IBM observed and effort from this run
  #if(t == 1) {
    IBM_observed_results[[t]] <- IBM_results[[t]]$all_observed
    IBM_effort_results[[t]] <- IBM_results[[t]]$all_effort
    # Correcting the quarters in the IBM that just ran if t > 1, after removing the final quarter (which is just the starting values)
    IBM_results[[t]]$all_quarters <- IBM_results[[t]]$all_quarters[IBM_results[[t]]$all_quarters$Quarter %in% c(1:erad_quarter_time_step),]
    if(t > 1) {
      IBM_results[[t]]$all_quarters$Quarter <- IBM_results[[t]]$all_quarters$Quarter + t
    }
    # Saving all IBM quarter results
    IBM_all_quarters <- rbind(IBM_all_quarters, IBM_results[[t]]$all_quarters)
      
    
  # } else {
  #   IBM_observed_results[[t]] <- c(IBM_observed_results[[t-1]]$all_observed,
  #                                    IBM_observed_results[[t]]$all_observed)
  #   IBM_effort_results[[t]] <- c(IBM_effort_results[[t-1]]$all_effort,
  #                                    IBM_effort_results[[t]]$all_effort)
  # }
  # Combining observations and efforts from all previous runs, and adjusting the quarters 
  combined_observed <- unlist(IBM_observed_results, recursive = FALSE)
  combined_effort <- unlist(IBM_effort_results, recursive = FALSE)
  for(quarter in 1:length(combined_observed)) {
    if(nrow(combined_observed[[quarter]]) > 0) {
    combined_observed[[quarter]]$quarter <- quarter
    } else {
      combined_observed[[quarter]][1,] <- NA
      combined_observed[[quarter]]$quarter <- NA
      combined_observed[[quarter]] <- combined_observed[[quarter]][0,]
    }
    combined_effort[[quarter]]$quarter <- quarter
  }
  # Combining the erad_days from all previous runs
  combined_erad_days <- unlist(estimation_effort_record$erad_days, recursive = FALSE)
  names(combined_erad_days) <- paste0("quarter_", c(1:length(combined_erad_days)))
  # Estimation model set up
  estimation_inputs <- estimation_inputs_fun(observed_list = combined_observed,
                                             effort_list = combined_effort)
  # Call JAGS Function
  output_jags <- jags(data = estimation_inputs$data,
                    inits = estimation_inputs$inits,
                    parameters.to.save = estimation_inputs$parameters,
                    "removal_model_alt_strategies.jags",
                    n.chains = nc,
                    n.thin = nt,
                    n.iter = ni,
                    n.burnin = nb)

  saveRDS(output_jags, file = here("Results", "alt_strategies", "Strategy_two", "Estimation",
  paste0("output_jags_test_", t, ".RDS")))
  # Mean N estimates vs simulated real N
  est_v_sim_N_plots <- estimated_N_plots(jags_output = output_jags,
                                         all_quarters = IBM_all_quarters,
                                         observed_erad_quarters = estimation_inputs$obs_quarters)


  ## Testing to see if any thresholds are met
  mean_N_df <- est_v_sim_N_plots$mean_N_df
  condition <- strat_2_threshold_fun(mean_N_df)
  # Advancing counter by the number of quarters that have been estimated
  t <- t+1
}
    


```

```{r strategy_2_parallel_attempt}

# Setting up parallel clusters
library(doParallel)
# Detect the number of clusters available
n_cores <- detectCores()
# Select half of them
cl <- makeCluster(n_cores/2)
registerDoParallel(cl)


# Using just one scenario to try running in parallel:
N_reps <- starting_pop[[1]]
size_dist <- starting_size_dist[[1]]
final_time_step <- 2 # one year to start with
# Running model variants in parallel
results <- foreach(variant = 1:8)  %dopar% {
  # Calling libraries needed (couldn't figure out how to attach them properly)
  library(dplyr)
  library(reshape2)
  library(ggplot2)
  library(dplyr)
  library(here)
  library(tictoc)
  library(fdrtool)
  library(jagsUI)
  library(scales)
  library(vctrs)
  # Setting starting N for this variant
  N <- N_reps[variant]
  # List to save IBM results outside of loop
  IBM_results <- list()
  IBM_observed_results <- list()
  IBM_effort_results <- list()
  IBM_all_quarters <- as.data.frame(matrix(nrow = 0, ncol = 8))
  colnames(IBM_all_quarters) <- c("ID", "sex", "repro_prob", "growth_quant", "variable", "SVL", "Quarter", "size_category")
  # Record of effort details as condition changes
  estimation_effort_record <- list()
  estimation_effort_record$condition <- vector()
  estimation_effort_record$primary_sampling_period <- list()
  estimation_effort_record$erad_quarters <- list()
  estimation_effort_record$erad_days <- list()
  # Starting condition
  condition <- "initial"
  # Starting counter
  t <- 1
  while(t <= final_time_step) {
    if(t == 1) { # First time step 
      # Separating out methods for initial condition
      new_methods <- method_options$initial
      # Setting parameter to run IBM initially
      run_type <- "initial"
      # Creating empty variable so function will run 
      last_quarter_df <- NULL
    } else {
      # Identifying methods condition 
      new_methods <- method_options[[condition]]
      # Isolating population from final time step to make the new initial population
      last_quarter_df <- IBM_results[[t-1]]$quarter_timeseries[[erad_quarter_time_step+1]]
      # Setting parameter to run IBM with existing population
      run_type <- "continuing"
    } 
    # Separating out parameters based on condition 
      methods <- new_methods$methods
      coverage <- new_methods$erad_coverage
      primary_sampling_period <- new_methods$primary_sampling_period
      erad_quarters <- new_methods$erad_quarters
      erad_days <- new_methods$erad_days
      ADS_overlap <- new_methods$ADS_overlap_on_transect
      num_teams <- new_methods$num_teams
      
      # Save method options 
      # Recording condition effort for next estimation round
    estimation_effort_record$condition[t] <- condition
    estimation_effort_record$primary_sampling_period[[t]] <- primary_sampling_period
    estimation_effort_record$erad_quarters[[t]] <- erad_quarters
    estimation_effort_record$erad_days[[t]] <- erad_days
      
      # Running IBM model with condition methods
      IBM_results[[t]] <- quarter_operations(initial_N = N, 
                                             initial_size_dist = size_dist, 
                                             p_g = g_density_prob,
                                             lambda = lambda,
                                             total_quarters = erad_quarter_time_step,
                                             total_days = day_time_step,
                                             erad = "on",
                                             erad_method =  methods,
                                             erad_coverage = coverage,
                                             primary_sampling_period = primary_sampling_period,
                                             erad_quarters = erad_quarters,
                                             erad_days = erad_days,
                                             ADS_overlap_on_transect = ADS_overlap,
                                             type_of_run = run_type,
                                             num_teams = num_teams,
                                             last_quarter_df = last_quarter_df)
    
    # Saving IBM observed and effort from this run
    #if(t == 1) {
      IBM_observed_results[[t]] <- IBM_results[[t]]$all_observed
      IBM_effort_results[[t]] <- IBM_results[[t]]$all_effort
      # Correcting the quarters in the IBM that just ran if t > 1, after removing the final quarter (which is just the starting values)
      IBM_results[[t]]$all_quarters <- IBM_results[[t]]$all_quarters[IBM_results[[t]]$all_quarters$Quarter %in% c(1:erad_quarter_time_step),]
      if(t > 1) {
        IBM_results[[t]]$all_quarters$Quarter <- IBM_results[[t]]$all_quarters$Quarter + t
      }
      
      # Save IBM results from this run
      saveRDS(IBM_results, file = here("Results", "alt_strategies", "Strategy_two", "IBM", paste0("IBM_results_parallel_test_variant-", variant, "_IBM_set-", t, ".rds")))
      
      # Saving all IBM quarter results
      IBM_all_quarters <- rbind(IBM_all_quarters, IBM_results[[t]]$all_quarters)
  
    # Combining observations and efforts from all previous runs, and adjusting the quarters 
    combined_observed <- unlist(IBM_observed_results, recursive = FALSE)
    combined_effort <- unlist(IBM_effort_results, recursive = FALSE)
    for(quarter in 1:length(combined_observed)) {
      if(nrow(combined_observed[[quarter]]) > 0) {
      combined_observed[[quarter]]$quarter <- quarter
      } else {
        combined_observed[[quarter]][1,] <- NA
        combined_observed[[quarter]]$quarter <- NA
        combined_observed[[quarter]] <- combined_observed[[quarter]][0,]
      }
      combined_effort[[quarter]]$quarter <- quarter
    }
    # Combining the erad_days from all previous runs
    combined_erad_days <- unlist(estimation_effort_record$erad_days, recursive = FALSE)
    names(combined_erad_days) <- paste0("quarter_", c(1:length(combined_erad_days)))
    # Estimation model set up
    estimation_inputs <- estimation_inputs_fun(observed_list = combined_observed,
                                               effort_list = combined_effort)
    # Call JAGS Function
    output_jags <- jags(data = estimation_inputs$data,
                      inits = estimation_inputs$inits,
                      parameters.to.save = estimation_inputs$parameters,
                      "removal_model_alt_strategies.jags",
                      n.chains = nc,
                      n.thin = nt,
                      n.iter = ni,
                      n.burnin = nb)
  
    saveRDS(output_jags, file = here("Results", "alt_strategies", "Strategy_two", "Estimation",
    paste0("output_jags_paralell_test_variant-",variant, "_est_", t, ".RDS")))
    # Mean N estimates vs simulated real N
    est_v_sim_N_plots <- estimated_N_plots(jags_output = output_jags,
                                           all_quarters = IBM_all_quarters,
                                           observed_erad_quarters = estimation_inputs$obs_quarters, 
                                           observed_erad_days = estimation_inputs$obs_days)
  
  
    ## Testing to see if any thresholds are met
    mean_N_df <- est_v_sim_N_plots$mean_N_df
    condition <- strat_2_threshold_fun(mean_N_df)
    # Advancing counter by the number of quarters that have been estimated
    t <- t+1
  }
  # Saving effort record and the IBM all_quarters data frame from the entire time period
  saveRDS(estimation_effort_record, file = here("Results", "alt_strategies", "Strategy_two", "IBM", "effort_record_variant-", variant, ".rds"))
  saveRDS(IBM_all_quarters, file = here("Results", "alt_strategies", "Strategy_two", "IBM", "IBM_all_quarters_variant-", variant, ".rds"))
  #estimation_effort_record$condition
}

# Testing
test_jags <- readRDS(file = here("Results", "alt_strategies", "Strategy_two", "Estimation",
    paste0("output_jags_paralell_test_variant-",2, "_est_", 2, ".RDS")))
test_IBM <- readRDS(file = here("Results", "alt_strategies", "Strategy_two", "IBM", paste0("IBM_results_parallel_test_variant-", 2, "_IBM_set-", 2, ".rds")))
all_quarters <- rbind(test_IBM[[1]]$all_quarters, test_IBM[[2]]$all_quarters)
all_days_1 <- unique(test_IBM[[1]]$all_effort[[1]]$day[test_IBM[[1]]$all_effort[[1]]$method %in% erad_methods[c(2:3)]],
                   test_IBM[[1]]$all_effort[[2]]$day[test_IBM[[1]]$all_effort[[2]]$method %in% erad_methods[c(2:3)]])
all_days_2 <- unique(test_IBM[[2]]$all_effort[[1]]$day[test_IBM[[2]]$all_effort[[1]]$method %in% erad_methods[c(2:3)]],
                   test_IBM[[2]]$all_effort[[2]]$day[test_IBM[[2]]$all_effort[[2]]$method %in% erad_methods[c(2:3)]])
all_days <- unique(all_days_1, all_days_2)
est_v_sim_plot <- estimated_N_plots(test_jags, all_quarters, c(1:4), all_days)


# Stop the cluster
stopCluster(cl = cl)

```

### Strategy 3: Eradication focus without ADS

A strategy with no ADS but a high amount of transect-based effort, geared towards eradication with relatively little monitoring, as ADS is a little precarious and could disappear (company that provides the materials is not entirely solvent, it sounds like). The only threshold is also geared towards eradication, but only on one size class to see if that would be sufficient to signal if the reproductively active part of the population is nearing or reaching eradication (as opposed to making the threshold based on the entire population).

-   Starting methods: Visual survey: high effort (9 weeks, 2 teams) per quarter; Trap: high effort (9 weeks) per quarter; Bait tubes: high effort (9 weeks) per quarter. 3 weeks of each quarter is only visual & trap, no bait tubes, to allow for monitoring

-   Threshold 1: estimated mean density of extra-large size class is 0 for \>=2 quarters

    -   If met: stop all methods for 2 quarters, do 1 rounds of low effort visual survey (2 weeks, 4 teams) in 3rd and 4th quarters

-   Estimate population every 4 quarters

-   Transect details:

    -   There are assumed to be 113 transects

    -   I assume that one team can do a visual survey OR check traps on 4 transects in 1 night, and one team can check bait tubes on 8 transects in 1 night

        -   This means that one team could survey or check traps on all transects in 29 days, or two teams could do it 15 days

    -   Visual surveys occur every other day for 9 weeks, but only 3 weeks of that is the primary sampling period (the other 6 weeks overlap with bait tubes)

        -   This means that 1 team can cover the entire area each quarter (some overlap would occur, but that wouldn't change the coverage parameter since 100% coverage is the maximum). It would change the encounter probability though - however, since 31 days is only 2 days more than 29, I'll operate as though encounter is based on just 1 team. Increasing effort, though, would require increasing the number of teams (and therefore the encounter probability), in the threshold 1 scenario

            -   Going with 100% coverage with four teams

    -   Traps are checked every 3rd day for the same 9 weeks (same overlapping with bait tubes as visual survey, so 3 weeks)

        -   Since traps are checked every 3 days, there are 21 effort days in this period, so two teams could cover the whole area (with 1 night requiring checking 5 transects), or one team could cover \~70% of the area each quarter. Encounter probability is the same though, because its based on the number of traps not the number of times they're checked (although the number of times they're checked would theoretically have an impact on encounter probability...whatever, not worth exploring now, since I don't think I have any data on that).

            -   Going with 100% coverage with two teams for now

    -   Bait tubes are checked and re-stocked every 3rd day for 9 weeks

        -   One team can check the entire area in each quarter

```{r strategy_3_define_thresholds}


#mean_N_df <- est_v_sim_N_plots$mean_N_df

strat_3_threshold_fun <- function(mean_N_df,
                                  xlarge_density = 0,
                                  area = area_size,
                                  size_class = size_class_names) {
  # Condition (default is initial)
  condition <- "initial"
  # Adding a column with density
  mean_N_df$mean_density <- mean_N_df$N/area
  # Identifying final time step 
  last_quarter <- tail(sort(unique(mean_N_df$Quarter)),1)
  # Separating final time step
  last_quarter_means <- mean_N_df[mean_N_df$Quarter == last_quarter, ]
  
  ## Calculating mean densities 
  # X-large size class
  xlarge_mean_density <- last_quarter_means$N[last_quarter_means$size_class == size_class[4]]/area
  
  
  ## Threshold 1: Estimated mean density is of x-large size class is <=0.01 snake/ha 
  if(xlarge_mean_density <= xlarge_density) {
    condition <- "threshold_1"
  }  
  
  return(condition)
}

```

```{r strategy_3_setup}

### Manually set IBM parameters
# Number of quarters to generate between estimation rounds - 1 year at a time
erad_quarter_time_step <- 4

# Methods for all evenatualities; starting, threshold 1, threshold 2 and threshold 3
method_option_names <- c("initial", "threshold_1")
method_options <- list()
for(option in 1:length(method_option_names)) {
  method_options[[option]] <- list()
}
names(method_options) <- method_option_names

# Identifying the methods that will be used under each of these conditions
method_options$initial$methods <- erad_methods[c(2:4)]
method_options$threshold_1$methods <- erad_methods[2]

## Quarters where eradication methods are used for each condition
# All methods used in all quarters for initial condition
method_options$initial$erad_quarters <- list()
for(method in method_options$initial$methods) {
  method_options$initial$erad_quarters[[method]] <- c(1:erad_quarter_time_step)
}

# Threshold 1: no methods used in the first 2 quarters, visual in later 2 quarters
method_options$threshold_1$erad_quarters <- list()
method_options$threshold_1$erad_quarters$visual <- c(3:4)

## Days where eradication methods are used for each condition
# Initial condition days
method_options$initial$erad_days <- list()
for(quarter in 1:erad_quarter_time_step) {
  method_options$initial$erad_days[[quarter]] <- list()
  # Visual survey: medium effort (9 weeks, 2 teams) per quarter - surveying every other day
  method_options$initial$erad_days[[quarter]]$visual <- seq(2, (7*10 - 1), 2)
  # Trap: medium effort (6 weeks) per quarter - checking traps every 3 days
  method_options$initial$erad_days[[quarter]]$trap <- seq(2, (7*10 - 1), 3)
  # Bait tubes: medium effort (6 weeks) per quarter
  method_options$initial$erad_days[[quarter]]$bait_tube <- seq(7*3, (7*12 - 1), 3)
}
names(method_options$initial$erad_days) <- paste0("quarter_", c(1:erad_quarter_time_step))

# Threshold 1 days (visual surveys only)
method_options$threshold_1$erad_days <- list()
for(quarter in 1:erad_quarter_time_step) {
  method_options$threshold_1$erad_days[[quarter]] <- list()
}
for(quarter in method_options$threshold_1$erad_quarters$visual) {
  # Visual survey: medium effort (6 weeks, 2 teams) per quarter - surveying every other day
  method_options$threshold_1$erad_days[[quarter]]$visual <- seq(2, 7*2, 2)
}
names(method_options$threshold_1$erad_days) <- paste0("quarter_", c(1:erad_quarter_time_step))


# Bounds of primary sampling periods for each condition (different for each)
method_options$initial$primary_sampling_period <- c(2,(7*3 - 1))
method_options$threshold_1$primary_sampling_period <- c(2, 7*2)


## Coverage for each method in a quarter for each condition
for(option in 1:length(method_options)) {
  method_options[[option]]$erad_coverage <- list()
  # even though there is no ADS in this strategy, this is a required parameter, and it doesn't actually impact anything
  method_options[[option]]$ADS_overlap_on_transect <- 1 
}
# Initial condition coverage
method_options$initial$erad_coverage$ADS <- 0 # necessary for a function, can fix this later
# Transect coverage (100%)
method_options$initial$erad_coverage$transects_per_quarter <- 1

# Threshold 1 condition coverage
method_options$threshold_1$erad_coverage$ADS <- 0 # necessary for a function, can fix this later
# Transect coverage (100% because effort is doubled) 
method_options$threshold_1$erad_coverage$transects_per_quarter <- 1


# Number of visual survey teams for each method
for(option in 1:length(method_options)) {
  method_options[[option]]$num_teams <- list()
}

method_options$initial$num_teams$visual <- 4
method_options$threshold_1$num_teams$visual <- 2

```

```{r strategy_3_run_IBM_once}

# Initial total N 
N <- starting_pop[[1]][1]
# Initial size distribution
size_dist <- starting_size_dist[[1]]

# Separating out condition 
methods <- method_options[[2]]$methods
coverage <- method_options[[2]]$erad_coverage
primary_sampling_period <- method_options[[2]]$primary_sampling_period
erad_quarters <- method_options[[2]]$erad_quarters
erad_days <- method_options[[2]]$erad_days
ADS_overlap <- method_options[[2]]$ADS_overlap_on_transect
num_teams <- method_options[[2]]$num_teams

# Running IBM model with initial conditions
erad_quarter_results <- quarter_operations(initial_N = N, 
                                           initial_size_dist = size_dist, 
                                           p_g = g_density_prob,
                                           lambda = lambda,
                                           total_quarters = erad_quarter_time_step,
                                           total_days = day_time_step,
                                           erad = "on",
                                           erad_method =  methods,
                                           erad_coverage = coverage,
                                           primary_sampling_period = primary_sampling_period,
                                           erad_quarters = erad_quarters,
                                           erad_days = erad_days,
                                           ADS_overlap_on_transect = ADS_overlap,
                                           type_of_run = "initial",
                                           num_teams = num_teams)

# Plotting the total population in each quarter
erad_plot_1 <- ggplot(erad_quarter_results$all_quarters, 
                      aes(x = Quarter, fill = size_category)) +
  geom_bar() +
  geom_hline(yintercept = K) +
  theme_bw() +
  scale_x_continuous(breaks = unique(erad_quarter_results$all_quarters$Quarter), labels = unique(erad_quarter_results$all_quarters$Quarter))

```

```{r strategy_3_run_estimation_once}

### Running estimation model once 

# Transforming multiple IBM runs into one dataset 

# Estimation model set up
estimation_inputs <- estimation_inputs_fun(erad_quarter_results$all_observed,
                                           erad_quarter_results$all_effort)

# Call JAGS Function
output_jags <- jags(data = estimation_inputs$data, 
                    inits = estimation_inputs$inits, 
                    parameters.to.save = estimation_inputs$parameters, 
                    "removal_model_simple_zero-inf.jags", 
                    n.chains = nc, 
                    n.thin = nt, 
                    n.iter = ni,
                    n.burnin = nb)

saveRDS(output_jags, file = here("Results", "alt_strategies", "Strategy_three", "Estimation",
"output_jags_test.RDS"))

# Parameter trace plots
traceplot(output_jags, parameters = c("r1", "r2", "r3", "r4"))
traceplot(output_jags, parameters = "p")
traceplot(output_jags, parameters = "psi")

# Mean N estimates vs simulated real N
est_v_sim_N_plots <- estimated_N_plots(jags_output = output_jags,
                                       all_quarters = erad_quarter_results$all_quarters,
                                       observed_erad_quarters = estimation_inputs$obs_quarters,
                                       observed_erad_days = estimation_inputs$obs_days)

## Testing to see if any thresholds are met
condition <- strat_3_threshold_fun(est_v_sim_N_plots$mean_N_df) 
```
