---
title: "Extended Generating Model"
author: "Kelly Mistry"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(fdrtool)
library(reshape2)
library(ggplot2)
library(tidyr)
library(here)
```

## Generating Model of Brown Treesnakes

Size-structured model with 4 size classes, with small snakes being less than 850 mm SVL (with a lower limit of 350 mm SVL at hatching), medium snakes being between 850 and 1150 mm SVL, large snakes being between 1150 and 1250 mm SVL, and extra large snakes being larger than 1250 mm SVL (based on the size classes that Staci used).

A time step in this model is 3 months, and the simulated population is based on the expected population in a 55 hectare area (the size of the HMU, the site of an eradication experiment in the near future).

The parameters I am estimating are:

-   growth of individuals ($\alpha_i$) in $i$ size class

-   reproduction ($r_i$) in $i$ size class

-   natural mortality ($d_i$) in $i$ size class

The entire population in time step $t$ ($N_t$) is defined as:

$$
N_t = \sum_{i = 1}^{4} n_{i,t}
$$

The population of the first size class in time step $t$ ($n_{1,t}$), is defined as:

$$
n_{i,t} = [1 - (\alpha_1 + d_1)] n_{1,t-1} + \sum_{i=2}^{4} r_i*n_{i, t-1}  
$$

The second size classes in time step $t$ ($n_{2,t}$) is defined as:

$$
n_{2,t} = [1-(\alpha_2 + d_2)]n_{2, t-1} + \alpha_1*n_{1,t-1}
$$

The third size classes in time step $t$ ($n_{3,t}$) is defined as:

$$
n_{3,t} = [1-(\alpha_3 + d_3)]n_{3, t-1} + \alpha_2*n_{2,t-1}
$$

The fourth and final size class in time step $t$ ($n_{4,t}$) is defined as:

$$
n_{4,t} = (1-d_4)n_{4,t-1} + \alpha_3*n_{3,t-1}
$$

#### Vital Rates

Growth rates are density dependent, using estimated carrying capacity ($K$) and peak *(or average, TBD)* growth rate for size class $i$ ($g_i$) constructed from the literature with a half normal relationship between density and growth. $n_t$ is the total population in time step $t$. Carrying capacity is used to construct the standard deviation of a half-normal distribution (with a mean of 0), $\theta$.

$$
\sigma = \frac{K*0.975}{1.96}
$$

$$
\theta =\frac{\sqrt{\pi/2}}{\sigma}
$$

Using this $\theta$, I calculated the probability density function of $n_t$ and scaled it by the PDF when density is 0, and then multiplied by the peak growth rate to produce a growth rate for size class $i$ at $n_t$, $\alpha_{i, n_t}$. Using the PDF equation for a half-normal distribution with a mean of 0 and standard deviation $\theta$, this becomes:

$$
\alpha_{i, n_t} = \frac{\frac{2\theta}{\pi}\exp(\frac{-n_t^2\theta^2}{\pi})}{\frac{2\theta}{\pi}\exp(\frac{0^2\theta^2}{\pi})}*g_i
$$

$$
\alpha_{i, n_t} = \frac{\exp(\frac{-n_t^2\theta^2}{\pi})}{\exp(0)}*g_i
$$

$$
\alpha_{i, n_t} = \exp(\frac{-n_t^2\theta^2}{\pi})*g_i
$$

Reproductive rates are also density dependent, and are calculated in the same way as growth rate, with peak reproductive rates for each size class constructed from the literature.

Natural mortality rates are constant for each size class, $d_i$, and are constructed from the literature.

**Details about how natural mortality, peak (or average) growth and reproductive rates were constructed from literature review can be found in vital_rates_lit_review.Rmd doc.**

```{r vital_rates_fun}


##### Vital rates function - use for both growth and reproductive rates

rates_fun <- function(carrying_capacity, 
                      peak_vital_rate,
                      current_density) {
  # Calculate sigma for scaling standard deviation using carrying capacity
  sd <- (carrying_capacity*0.975)/1.96
  # Calculate PDF when density is 0 (highest density probability value)
  max_prob_value <- dhalfnorm(0, theta = ((sqrt(pi/2))/sd))
  # Calculate PDF value for the current density
  PDf_value <- dhalfnorm(current_density, theta = ((sqrt(pi/2))/sd))
  # Use maximum value to scale current density's PDF value, and multiply by the peak vital rate
  rate <- (PDf_value/max_prob_value)*peak_vital_rate
  return(rate)
}

# Testing:
# x <- rates_fun(carrying_capacity = 6000, # from 116 snakes/hectare for 55 hectares
#           peak_vital_rate = 0.09216, # peak growth rate for small & medium sizes
#           current_density = 1000) 

```

```{r generating_model_fun}

### Function to generate population for all size classes in next time step 
generate_fun <- function(t_minus_1,# The previous time step data (1 row, 4 columns for each size class)
                            growth, # growth rate vector for 3 smaller size classes
                            mortality, # mortality rate vector for all size classes
                            reproduction) { # reproductive rate vector for 3 larger size classes
  # Create vector to hold the current time step's population numbers
  t <- vector() 
  # Calculate small class population (if population is less than 1, set to 0)
  t[1] <- (1-(growth[1] + mortality[1]))*t_minus_1[, 1] + 
    reproduction[1]*t_minus_1[, 2] + 
    reproduction[2]*t_minus_1[, 3] +
    reproduction[3]*t_minus_1[, 4]
  if(t[1] >= 1) {
    t[1] <- t[1]
  } else { 
    t[1] <- 0
  }
  # Calculate medium class population (if population is less than 1, set to 0)
  t[2] <- (1-(growth[2] + mortality[2]))*t_minus_1[, 2] +
    growth[1]*t_minus_1[, 1]
  if(t[2] >= 1) {
    t[2] <- t[2]
  } else {
    t[2] <- 0
  }
  # Calculate large class population (if population is less than 1, set to 0)
  t[3] <- (1-(growth[3] + mortality[3]))*t_minus_1[, 3] +
    growth[2]*t_minus_1[, 2]
  if(t[3] >= 1) {
    t[3] <- t[3]
  } else {
    t[3] <- 0
  }
  # Calculate x-large class population (if population is less than 1, set to 0)
  t[4] <- (1 - mortality[4])*t_minus_1[, 4] +
    growth[3]*t_minus_1[, 3]
  if(t[4] >= 1) {
    t[4] <- t[4]
  } else {
    t[4] <- 0
  }
  
  return(t)
}



```

### Generating model experimentation

```{r population_generation}

# Loading vital rates parameters constructed from literature (per Vital_rates_lit_review.Rmd)
rates_list <- readRDS("vital_rates_lit.rds")

# Separating out vital rates into separate vectors:
growth_peak_rates <- rates_list$growth_rates
repro_vector <- rates_list$repro_rates
mortality_vector <- rates_list$mortality_rates

# Number of years to simulate (with 4 time steps per year)
Year <- 100

# Starting population
N <- 6000

# Size classes
bins <- c("small",
          "medium",
          "large",
          "xlarge")
n_bins <- length(bins)

# Standard deviation of stochastic process
sd <- 5

# List of empty matrices to fill with growth and reproduction values drawn for each size class in each year
vital_rates <- list()
vital_rates$growth <- as.data.frame(matrix(NA, nrow = Year*4, ncol = 3))
colnames(vital_rates$growth) <- bins[-4]
vital_rates$repro <- as.data.frame(matrix(NA, nrow = Year*4, ncol = 3))
colnames(vital_rates$repro) <- bins[-1]

# Empty matrix to fill with population results for timeseries
# A column for each size class, plus a totals column
timeseries <- as.data.frame(matrix(NA, nrow = Year*4, ncol = n_bins+1))
colnames(timeseries) <- c(bins, "total")

# Time 0 in first row
timeseries[1, ] <- c(rep(N/4, 4), N)

for(ts in 2:(Year*4)) {
  # Generate growth rate for this year
  vital_rates$growth[ts-1, ] <- rates_fun(carrying_capacity = 6000,
          peak_vital_rate = growth_peak_rates,
          current_density = timeseries$total[ts-1])
  vital_rates$repro[ts-1, ] <- rates_fun(carrying_capacity = 6000,
          peak_vital_rate = repro_vector,
          current_density = timeseries$total[ts-1])
  # Generate next time step populations
  timeseries[ts, 1:4] <- unlist(generate_fun(t_minus_1 = timeseries[ts-1,],
                                       growth = vital_rates$growth[ts-1, ],
                                       mortality = mortality_vector,
                                       reproduction = vital_rates$repro[ts-1, ])) + rnorm(4, 0, sd)
  timeseries$total[ts] <- sum(timeseries[ts, 1:4])
}

# Adding year and quarter columns
timeseries$year <- rep(1:Year, each = 4)
timeseries$quarter <- rep(paste0("Q", 1:4), Year)

### Plotting all populations to see what's happening

# Melt matrix to make plotting easier
tm_plot <- melt(timeseries[, -5], id.vars = c("year", "quarter"))
colnames(tm_plot)[3:4] <- c("size", "pop")

ggplot(tm_plot, aes(fill = quarter, y = pop, x = year)) +
  geom_bar(position="dodge", stat="identity") +
  facet_wrap(vars(size)) +
  theme_bw()


## Plotting growth rates for each size class through time
vital_rates$growth$year <- rep(1:Year, each = 4)

growth_rates_plots <- melt(vital_rates$growth[-(Year*4),], id.vars = c("year"))
colnames(growth_rates_plots)[2:3] <- c("size", "growth_rate")

ggplot(growth_rates_plots, aes(x = year, y = growth_rate)) +
  geom_line()+
  facet_wrap(vars(size)) +
  theme_bw()

## Plotting reproductive rates for each size class through time
vital_rates$repro$year <- rep(1:Year, each = 4)

repro_rates_plots <- melt(vital_rates$repro[-(Year*4),], id.vars = c("year"))
colnames(repro_rates_plots)[2:3] <- c("size", "repro_rate")

ggplot(repro_rates_plots, aes(x = year, y = repro_rate)) +
  geom_line()+
  facet_wrap(vars(size)) +
  theme_bw()

## Plotting proportion of size classes in population
# Adding timestep to make it easier to plot as continuous through time
tm_plot$time_step <- rep(1:(Year*4), 4)

init_plot <- ggplot(tm_plot, aes(fill = size, y = pop, x = time_step)) +
  geom_bar(position="stack", stat="identity") +
  theme_bw()
# Saving plot
ggsave(filename = "initial_pop_plot.png", plot = init_plot,
       path = here("Results"))
  
```

### Sensitivity Analyses

#### Starting population

Trying out a number of different starting populations to see how the model behaves

```{r starting_pop}
# Starting population list to iterate over 
N_options <- unique(c(seq(100, 1100, 200), seq(500, 7500, 750))) # 15 scenarios
# Vector of names for lists of results by starting population
SP_list_names <- paste0("SP_", N_options)

##### Parameters that won't change
# Number of years (with 4 time steps per year)
Year <- 100
# Loading vital rates parameters
rates_list <- readRDS("vital_rates_lit.rds")
# Separating out vital rates into separate vectors:
growth_peak_rates <- rates_list$growth_rates
repro_vector <- rates_list$repro_rates
mortality_vector <- rates_list$mortality_rates
# Size classes
bins <- c("small",
          "medium",
          "large",
          "xlarge")
n_bins <- length(bins)
# Standard deviation of stochastic process
sd <- 5

### Lists to store vital rates and population by size as they change through time
all_vital_rates <- list()
all_timeseries <- list()


### Loops
## Within each loop: set starting population, create dataframes to hold growth and reproductive rates, and the population numbers through time. Then, run model for Year*4 time series with each startig population value, and save the population results and the growth & reproduction values through time

for(sp in 1:length(N_options)) {
  # Set starting population
  N <- N_options[sp]
  # Create list of empty dataframes to hold vital rates
  vital_rates <- list()
  vital_rates$growth <- as.data.frame(matrix(NA, nrow = Year*4, ncol = 3))
  colnames(vital_rates$growth) <- bins[-4]
  vital_rates$repro <- as.data.frame(matrix(NA, nrow = Year*4, ncol = 3))
  colnames(vital_rates$repro) <- bins[-1]
  # Create empty dataframe for population timeseries
  timeseries <- as.data.frame(matrix(NA, nrow = Year*4, ncol = n_bins+1))
  colnames(timeseries) <- c(bins, "total")
  # Time 0 in first row
  timeseries[1, ] <- c(rep(N/4, 4), N)
  
  for(ts in 2:(Year*4)) {
    # Generate growth rate for this year
    vital_rates$growth[ts-1, ] <- rates_fun(carrying_capacity = 6000,
                                            peak_vital_rate = growth_peak_rates,
                                            current_density = timeseries$total[ts-1])
    vital_rates$repro[ts-1, ] <- rates_fun(carrying_capacity = 6000,
                                           peak_vital_rate = repro_vector,
                                           current_density = timeseries$total[ts-1])
    # Generate next time step populations
    timeseries[ts, 1:4] <- unlist(generate_fun(t_minus_1 = timeseries[ts-1,],
                                               growth = vital_rates$growth[ts-1, ],
                                               mortality = mortality_vector,
                                               reproduction = vital_rates$repro[ts-1, ])) + rnorm(4, 0, sd)
    timeseries$total[ts] <- sum(timeseries[ts, 1:4])
  }
  # Adding year and quarter columns
  timeseries$year <- rep(1:Year, each = 4)
  timeseries$quarter <- rep(paste0("Q", 1:4), Year)
  
  # Saving timeseries to list
  all_timeseries[[sp]] <- timeseries
  # Saving vital rate dataframes
  all_vital_rates[[sp]] <- vital_rates
  
}

names(all_timeseries) <- SP_list_names
names(all_vital_rates) <- SP_list_names

#### Creating and saving plots of growth rate, reproductive rate and populations through time

for(sp in SP_list_names) {
  # Restructuring growth rate results for plotting
  all_vital_rates[[sp]]$growth$year <- rep(1:Year, each = 4)
  growth_rates_plots <- melt(all_vital_rates[[sp]]$growth[-(Year*4),], id.vars = c("year"))
  colnames(growth_rates_plots)[2:3] <- c("size", "growth_rate")
  # Creating growth rate plot
  growth_plot <- ggplot(growth_rates_plots, aes(x = year, y = growth_rate)) +
    geom_line()+
    facet_wrap(vars(size)) +
    theme_bw() +
    labs(title = sp)
  #### Saving plots to file
  ggsave(filename = paste0(sp, "_growth.png"), plot = growth_plot,
       path = here("Results/sensitivity_analyses/starting_pop/Plots/Growth"))
  
  # Restructuring reproductive rate results for plotting
  all_vital_rates[[sp]]$repro$year <- rep(1:Year, each = 4)
  repro_rates_plots <- melt(all_vital_rates[[sp]]$repro[-(Year*4),], id.vars = c("year"))
  colnames(repro_rates_plots)[2:3] <- c("size", "repro_rate")
  
  reproductive_plot <- ggplot(repro_rates_plots, aes(x = year, y = repro_rate)) +
    geom_line()+
    facet_wrap(vars(size)) +
    theme_bw() +
    labs(title = sp)
  #### Saving plots to file
  ggsave(filename = paste0(sp, "_repro.png"), plot = reproductive_plot,
       path = here("Results/sensitivity_analyses/starting_pop/Plots/Reproduction"))
  
  ## Plotting proportion of size classes in population through timeseries
  # restructuring timeseries data for plotting, and adding timestep
  tm_plot <- melt(all_timeseries[[sp]][, -5], id.vars = c("year", "quarter"))
  colnames(tm_plot)[3:4] <- c("size", "pop")
  tm_plot$time_step <- rep(1:(Year*4), 4)
  # Creating population timeseries plot
  population_plot <- ggplot(tm_plot, aes(fill = size, y = pop, x = time_step)) +
    geom_bar(position="stack", stat="identity") +
    theme_bw() +
    labs(title = sp)
  #### Saving plots to file
  ggsave(filename = paste0(sp, "_pop.png"), plot = population_plot,
       path = here("Results/sensitivity_analyses/starting_pop/Plots/Population"))
}

### Plots comparing the final population and vital rate values from each starting population scenario
# Pulling out final population numbers
final_pop <- as.data.frame(matrix(NA, nrow = length(N_options), ncol = ncol(all_timeseries[[1]])))
colnames(final_pop) <- colnames(all_timeseries[[1]])

for(sp in 1:length(SP_list_names)) {
  final_pop[sp, ] <- all_timeseries[[sp]][Year*4, ]
}
final_pop$scenario <- SP_list_names
# Melting data for plotting
final_pop_melt <- melt(final_pop[, -c(5:7)], id.vars = "scenario")
colnames(final_pop_melt)[2:3] <- c("size", "pop")
# Making scenarios into ordered factors for clarity
final_pop_melt$scenario <- factor(final_pop_melt$scenario, levels = SP_list_names)

final_ts_plot <- ggplot(final_pop_melt, aes(y = pop, x = scenario, fill = size)) +
  geom_bar(position="stack", stat="identity") +
  theme_bw() +
  theme(axis.text.x=element_text(angle = -90, hjust = 0))

# Saving plot
ggsave(filename = "final_ts_pop_comparison.png", plot = final_ts_plot, path = here("Results/sensitivity_analyses/starting_pop/Plots"))

# Pulling out final growth rate numbers
final_growth <- as.data.frame(matrix(NA, nrow = length(N_options), ncol = ncol(all_vital_rates[[1]]$growth)))
colnames(final_growth) <- colnames(all_vital_rates[[1]]$growth)

for(sp in 1:length(SP_list_names)) {
  final_growth[sp, ] <- all_vital_rates[[sp]]$growth[(Year*4-1), ]
}
final_growth$scenario <- SP_list_names
# Melting data for plotting
final_growth_melt <- melt(final_growth, id.vars = c("scenario"))
colnames(final_growth_melt)[2:3] <- c("size", "growth_rate")
# Making scenarios into ordered factors for clarity
final_growth_melt$scenario <- factor(final_growth_melt$scenario, levels = SP_list_names)
# Creating growth rate plot
growth_plot <- ggplot(final_growth_melt, aes(x = size, y = growth_rate, fill = scenario)) +
    geom_bar(position="dodge", stat="identity") +
    theme_bw()

# Saving plot
ggsave(filename = "final_ts_growth_comparison.png", plot = growth_plot, path = here("Results/sensitivity_analyses/starting_pop/Plots"))

# Pulling out final reproductive rate numbers
final_repro <- as.data.frame(matrix(NA, nrow = length(N_options), ncol = ncol(all_vital_rates[[1]]$repro)))
colnames(final_repro) <- colnames(all_vital_rates[[1]]$repro)

for(sp in 1:length(SP_list_names)) {
  final_repro[sp, ] <- all_vital_rates[[sp]]$repro[(Year*4-1), ]
}
final_repro$scenario <- SP_list_names

# Melting data for plotting
final_repro_melt <- melt(final_repro, id.vars = c("scenario"))
colnames(final_repro_melt)[2:3] <- c("size", "growth_rate")
# Making scenarios into ordered factors for clarity
final_repro_melt$scenario <- factor(final_repro_melt$scenario, levels = SP_list_names)
# Creating growth rate plot
repro_plot <- ggplot(final_repro_melt, aes(x = size, y = growth_rate, fill = scenario)) +
    geom_bar(position="dodge", stat="identity") +
    theme_bw()

# Saving plot
ggsave(filename = "final_ts_repro_comparison.png", plot = repro_plot, path = here("Results/sensitivity_analyses/starting_pop/Plots"))


```

#### Size Distribution

Trying out different starting size distributions to see how that affects the model outputs

The starting population used here is 6000, initially (may change this based on the results, but I don't want the populations to die out too fast if I start too low)

```{r size_dist}

# Starting size distribution
init_size_dist_options <- list()
# One size class starts with 0
init_size_dist_options[[1]] <- c(0, rep(1/3, 3))
init_size_dist_options[[2]] <- c(1/3, 0, rep(1/3, 2))
init_size_dist_options[[3]] <- c(rep(1/3, 2), 0, 1/3)
init_size_dist_options[[4]] <- c(rep(1/3, 3), 0)
# One small size class, the other 3 equally sized
init_size_dist_options[[5]] <- c(0.2, rep((1-0.2)/3, 3))
init_size_dist_options[[6]] <- c((1-0.2)/3, 0.2, rep((1-0.2)/3, 2))
init_size_dist_options[[7]] <- c(rep((1-0.2)/3, 2), 0.2, (1-0.2)/3)
init_size_dist_options[[8]] <- c(rep((1-0.2)/3, 3), 0.2)
# One large size class, the other 3 equally sized
init_size_dist_options[[9]] <- c(0.8, rep((1-0.8)/3, 3))
init_size_dist_options[[10]] <- c((1-0.8)/3, 0.8, rep((1-0.8)/3, 2))
init_size_dist_options[[11]] <- c(rep((1-0.8)/3, 2), 0.8, (1-0.8)/3)
init_size_dist_options[[12]] <- c(rep((1-0.8)/3, 3), 0.8)
# Two small size classes, two large size classes
init_size_dist_options[[13]] <- c(rep(0.8/2, 2), rep((1-0.8)/2, 2))
init_size_dist_options[[14]] <- c(0.8/2, (1-0.8)/2, 0.8/2, (1-0.8)/2)
init_size_dist_options[[15]] <- c(0.8/2, (1-0.8)/2, (1-0.8)/2, 0.8/2)
init_size_dist_options[[16]] <- c((1-0.8)/2, 0.8/2, (1-0.8)/2, 0.8/2)
init_size_dist_options[[17]] <- c((1-0.8)/2, 0.8/2, 0.8/2, (1-0.8)/2)
init_size_dist_options[[18]] <- c(rep((1-0.8)/2, 2), rep(0.8/2, 2))

# Vector of names for lists of results by starting population
SSD_list_names <- vector()
for(i in 1:length(init_size_dist_options)) {
  SSD_list_names[i] <- paste0("SSD_", paste0(round(init_size_dist_options[[i]], 2), sep = "_", collapse = "" ))
}


##### Parameters that won't change
# Starting population 
N <- 1000
# Number of years (with 4 time steps per year)
Year <- 100
# Loading vital rates parameters
rates_list <- readRDS("vital_rates_lit.rds")
# Separating out vital rates into separate vectors:
growth_peak_rates <- rates_list$growth_rates
repro_vector <- rates_list$repro_rates
mortality_vector <- rates_list$mortality_rates
# Size classes
bins <- c("small",
          "medium",
          "large",
          "xlarge")
n_bins <- length(bins)
# Standard deviation of stochastic process
sd <- 5

### Lists to store vital rates and population by size as they change through time
all_vital_rates <- list()
all_timeseries <- list()


### Loops
## Within each loop: set starting population, create dataframes to hold growth and reproductive rates, and the population numbers through time. 

for(ssd in 1:length(init_size_dist_options)) {
  # Set starting size distribution
  init_size_dist <- init_size_dist_options[[ssd]]
  # Create list of empty dataframes to hold vital rates
  vital_rates <- list()
  vital_rates$growth <- as.data.frame(matrix(NA, nrow = Year*4, ncol = 3))
  colnames(vital_rates$growth) <- bins[-4]
  vital_rates$repro <- as.data.frame(matrix(NA, nrow = Year*4, ncol = 3))
  colnames(vital_rates$repro) <- bins[-1]
  # Create empty dataframe for population timeseries
  timeseries <- as.data.frame(matrix(NA, nrow = Year*4, ncol = n_bins+1))
  colnames(timeseries) <- c(bins, "total")
  # Time 0 in first row
  timeseries[1, ] <- c(N*init_size_dist, N)
  
  for(ts in 2:(Year*4)) {
    # Generate growth rate for this year
    vital_rates$growth[ts-1, ] <- rates_fun(carrying_capacity = 6000,
                                            peak_vital_rate = growth_peak_rates,
                                            current_density = timeseries$total[ts-1])
    vital_rates$repro[ts-1, ] <- rates_fun(carrying_capacity = 6000,
                                           peak_vital_rate = repro_vector,
                                           current_density = timeseries$total[ts-1])
    # Generate next time step populations
    timeseries[ts, 1:4] <- unlist(generate_fun(t_minus_1 = timeseries[ts-1,],
                                               growth = vital_rates$growth[ts-1, ],
                                               mortality = mortality_vector,
                                               reproduction = vital_rates$repro[ts-1, ])) + rnorm(4, 0, sd)
    timeseries$total[ts] <- sum(timeseries[ts, 1:4])
  }
  # Adding year and quarter columns
  timeseries$year <- rep(1:Year, each = 4)
  timeseries$quarter <- rep(paste0("Q", 1:4), Year)
  
  # Saving timeseries to list
  all_timeseries[[ssd]] <- timeseries
  # Saving vital rate dataframes
  all_vital_rates[[ssd]] <- vital_rates
  
}

names(all_timeseries) <- SSD_list_names
names(all_vital_rates) <- SSD_list_names

#### Creating and saving plots of growth rate, reproductive rate and populations through time

for(ssd in SSD_list_names) {
  # Restructuring growth rate results for plotting
  all_vital_rates[[ssd]]$growth$year <- rep(1:Year, each = 4)
  growth_rates_plots <- melt(all_vital_rates[[ssd]]$growth[-(Year*4),], id.vars = c("year"))
  colnames(growth_rates_plots)[2:3] <- c("size", "growth_rate")
  # Creating growth rate plot
  growth_plot <- ggplot(growth_rates_plots, aes(x = year, y = growth_rate)) +
    geom_line()+
    facet_wrap(vars(size)) +
    theme_bw() +
    labs(title = ssd)
  #### Saving plots to file
  ggsave(filename = paste0(ssd, "_growth.png"), plot = growth_plot,
       path = here("Results/sensitivity_analyses/size_dist/Plots/Growth"))
  
  # Restructuring reproductive rate results for plotting
  all_vital_rates[[ssd]]$repro$year <- rep(1:Year, each = 4)
  repro_rates_plots <- melt(all_vital_rates[[ssd]]$repro[-(Year*4),], id.vars = c("year"))
  colnames(repro_rates_plots)[2:3] <- c("size", "repro_rate")
  
  reproductive_plot <- ggplot(repro_rates_plots, aes(x = year, y = repro_rate)) +
    geom_line()+
    facet_wrap(vars(size)) +
    theme_bw() +
    labs(title = ssd)
  #### Saving plots to file
  ggsave(filename = paste0(ssd, "_repro.png"), plot = reproductive_plot,
       path = here("Results/sensitivity_analyses/size_dist/Plots/Reproduction"))
  
  ## Plotting proportion of size classes in population through timeseries
  # restructuring timeseries data for plotting, and adding timestep
  tm_plot <- melt(all_timeseries[[ssd]][, -5], id.vars = c("year", "quarter"))
  colnames(tm_plot)[3:4] <- c("size", "pop")
  tm_plot$time_step <- rep(1:(Year*4), 4)
  # Creating population timeseries plot
  population_plot <- ggplot(tm_plot, aes(fill = size, y = pop, x = time_step)) +
    geom_bar(position="stack", stat="identity") +
    theme_bw() +
    labs(title = ssd)
  #### Saving plots to file
  ggsave(filename = paste0(ssd, "_pop.png"), plot = population_plot,
       path = here("Results/sensitivity_analyses/size_dist/Plots/Population"))
}

### Plots comparing the final population and vital rate values from each starting population scenario
# Pulling out final population numbers
final_pop <- as.data.frame(matrix(NA, nrow = length(init_size_dist_options), ncol = ncol(all_timeseries[[1]])))
colnames(final_pop) <- colnames(all_timeseries[[1]])

for(ssd in 1:length(SSD_list_names)) {
  final_pop[ssd, ] <- all_timeseries[[ssd]][Year*4, ]
}
final_pop$scenario <- SSD_list_names
# Melting data for plotting
final_pop_melt <- melt(final_pop[, -c(5:7)], id.vars = "scenario")
colnames(final_pop_melt)[2:3] <- c("size", "pop")
# Making scenarios into ordered factors for clarity
final_pop_melt$scenario <- factor(final_pop_melt$scenario, levels = SSD_list_names)

final_ts_plot <- ggplot(final_pop_melt, aes(y = pop, x = scenario, fill = size)) +
  geom_bar(position="stack", stat="identity") +
  theme_bw() +
  theme(axis.text.x=element_text(angle = -90, hjust = 0))

# Saving plot
ggsave(filename = "final_ts_pop_comparison.png", plot = final_ts_plot, path = here("Results/sensitivity_analyses/size_dist/Plots"))

# Pulling out final growth rate numbers
final_growth <- as.data.frame(matrix(NA, nrow = length(init_size_dist_options), ncol = ncol(all_vital_rates[[1]]$growth)))
colnames(final_growth) <- colnames(all_vital_rates[[1]]$growth)

for(ssd in 1:length(SSD_list_names)) {
  final_growth[ssd, ] <- all_vital_rates[[ssd]]$growth[(Year*4-1), ]
}
final_growth$scenario <- SSD_list_names
# Melting data for plotting
final_growth_melt <- melt(final_growth[, -4], id.vars = c("scenario"))
colnames(final_growth_melt)[2:3] <- c("size", "growth_rate")
# Making scenarios into ordered factors for clarity
final_growth_melt$scenario <- factor(final_growth_melt$scenario, levels = SSD_list_names)
# Creating growth rate plot
growth_plot <- ggplot(final_growth_melt, aes(x = size, y = growth_rate, fill = scenario)) +
    geom_bar(position="dodge", stat="identity") +
    theme_bw()

# Saving plot
ggsave(filename = "final_ts_growth_comparison.png", plot = growth_plot, path = here("Results/sensitivity_analyses/size_dist/Plots"))

# Pulling out final reproductive rate numbers
final_repro <- as.data.frame(matrix(NA, nrow = length(init_size_dist_options), ncol = ncol(all_vital_rates[[1]]$repro)))
colnames(final_repro) <- colnames(all_vital_rates[[1]]$repro)

for(ssd in 1:length(SSD_list_names)) {
  final_repro[ssd, ] <- all_vital_rates[[ssd]]$repro[(Year*4-1), ]
}
final_repro$scenario <- SSD_list_names

# Melting data for plotting
final_repro_melt <- melt(final_repro[, -4], id.vars = c("scenario"))
colnames(final_repro_melt)[2:3] <- c("size", "growth_rate")
# Making scenarios into ordered factors for clarity
final_repro_melt$scenario <- factor(final_repro_melt$scenario, levels = SSD_list_names)
# Creating growth rate plot
repro_plot <- ggplot(final_repro_melt, aes(x = size, y = growth_rate, fill = scenario)) +
    geom_bar(position="dodge", stat="identity") +
    theme_bw()

# Saving plot
ggsave(filename = "final_ts_repro_comparison.png", plot = repro_plot, path = here("Results/sensitivity_analyses/size_dist/Plots"))

```
