---
title: "Vital Rates Lit Review"
author: "Kelly Mistry"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## BTS Vital Rates from Literature Review

### Growth rate between size classes

### Reproductive rate

Both female and male BTS can potentially reproduce year-round on Guam, although their reproduction is seasonal in their native ranges (Savidge et al. 2007, Mathies et al. 2010)

*Size at sexual maturity (which of my size classes can reproduce)*

-   Savidge et al. 2007:

    -   90% of females were sexually mature at 910 - 1,025 mm SVL (min = 840, max = 1,110) and 90% of males matured from 940 - 1,030 mm SVL (min = 805, max = 1,135)

-   *Number of females in the population who reproduce*

```{=html}
<!-- -->
```
-   Nafus et al. 2021:

    -   Most females only produced once during study (October 2016 - March 2017)

*How many times per year a reproducing female produces a clutch*

-   Nafus et al. 2021:

    -   For females that produced more than once during study, they had one clutch per year

*Clutch size (or number of follicles which could become eggs)*

-   Savidge et al. 2007:

    -   Mean clutch size (14 snakes, based on follicles rather than eggs except in 1 case) is 4.3, sd = 2.2, range 2- 9

-   Rodda et al. 1999:

    -   BTS mean clutch size in native ranges are 4-12, 7 and 5.5

-   Nafus et al. 2021:

    -   an average of 11 follicles for each female juvenile observed, which suggests that 9% (1 out of 11) detected follicles resulted in a female snake

-   Kahl et al. 2012:

    -   Clutch size varies widely across native range (between 3 and 11), with an average of 5.5

    -   Not enough data for a real estimate, but the few clutches found on Guam have had 3 or 4 eggs, with up to 8

*Relationship between size and reproductive capacity*

-   Mathies et al. 2010:

    -   Lots of individual variation in testosterone levels, but not related to body mass

```{=html}
<!-- -->
```
-   Rodda et al. 1999:

    -   Correlation between maternal size and number of eggs found in Australian BTS

-   Kahl et al. 2012:

    -   Larger females lay large clutches

*Incubation length*

-   Rodda et al. 1999:

    -   Egg incubation is likely 75 - 90 days

-   Kahl et al. 2012:

    -   In Australia, incubation took from 76 to 90 days, depending on temperature

    -   Incubation periods on Guam have been longer, from 94 to 126 days

```{r reproduction}

```

### Natural Mortality rate
