---
title: "Brown Tree Snakes - Initial Models"
author: "Kelly Mistry"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(reshape2)
library(ggplot2)
library(tidyr)
```

## Basic Brown Tree Snakes management model

### First step: Generating model

Size-structured model with 4 size classes. The simplest version I'll start with is has growth rates between size classes, reproductive rates for the 3 larger size classes and death rates for all. The model is discrete, with a time step equaling 3 months.

The entire population in time step t ($N_t$) is defined as:

$$
N_t = \sum_{i = 1}^{4} n_{i,t}
$$

The population of the first size class in time step t ($n_{1,t}$), is defined as:

$$
n_{i,t} = [1 - (\alpha_1 + d_1)] n_{1,t-1} + \sum_{i=2}^{4} r_i*n_{i, t-1}  
$$

The second size classes in time step t ($n_{2,t}$) is defined as:

$$
n_{2,t} = [1-(\alpha_2 + d_2)]n_{2, t-1} + \alpha_1*n_{1,t-1}
$$

The third size classes in time step t ($n_{3,t}$) is defined as:

$$
n_{3,t} = [1-(\alpha_3 + d_3)]n_{3, t-1} + \alpha_2*n_{2,t-1}
$$

The fourth and final size class in time step t ($n_{4,t}$) is defined as:

$$
n_{4,t} = (1-d_4)n_{4,t-1} + \alpha_3*n_{3,t-1}
$$

Initial conditions, just to get the model going:

-   $N_0$ = 100, with 25 in each size class

-   all growth rates, $\alpha$, = 0.2

-   all reproductive rates, $r$, = 0.3

-   all death rates, $d$, = 0.1

-   80 time steps (20 years)

```{r generating_model}
# Total starting population
N <- 100

# Size classes
bins <- c("small",
          "medium",
          "large",
          "xlarge")
n_bins <- length(bins)

# Starting population proportions for each size class
n_1_prop <- 0.25
n_2_prop <- 0.25
n_3_prop <- 0.25
n_4_prop <- 0.25

# Vector of starting populations in each size class
n_vector <- c("n_1" = N*n_1_prop, # small
              "n_2" = N*n_2_prop, # medium
              "n_3" = N*n_3_prop, # large
              "n_4" = N*n_4_prop) # x-large


# Vector of growth rate for each size class
growth_vector <- c("alpha_1" = 0.2, # growth from small to medium
                   "alpha_2" = 0.2, # growth from medium to large
                   "alpha_3" = 0.2) # growth from large to x-large

# Vector of natural mortality rates for each size class
mortality_vector <- c("d_1" = 0.1, 
                      "d_2" = 0.1, 
                      "d_3" = 0.1,
                      "d_4" = 0.1)

# Vector of reproductive rates for the 3 bigger size classes
repro_vector <- c("r_2" = 0.2, # reproductive rate for medium
                  "r_3" = 0.2, # reproductive rate for large
                  "r_4" = 0.2) # reproductive rate for x-large

# Number of years to simulate (with 4 time steps per year)
Year <- 20

# Empty matrix to fill with population results for a 20 year timeseries
# A column for each size class, plus a totals column
timeseries <- as.data.frame(matrix(NA, nrow = Year*4, ncol = n_bins+1))
colnames(timeseries) <- c(bins, "total")

# Time 0 in first row
timeseries[1, ] <- c(n_vector, N)

# Calculate population through time
for(year in 2:nrow(timeseries)) {
  # Calculate small class population
  timeseries[year, 1] <- (1-(growth_vector[1] + mortality_vector[1]))*timeseries[year-1, 1] + 
    repro_vector[1]*timeseries[year-1, 2] + 
    repro_vector[2]*timeseries[year-1, 3] +
    repro_vector[3]*timeseries[year-1, 4]
  # Calculate medium class population
  timeseries[year, 2] <- (1-(growth_vector[2] + mortality_vector[2]))*timeseries[year-1, 2] +
    growth_vector[1]*timeseries[year-1, 1]
  # Calculate large class population
  timeseries[year, 3] <- (1-(growth_vector[3] + mortality_vector[3]))*timeseries[year-1, 3] +
    growth_vector[2]*timeseries[year-1, 2]
  # Calculate x-large class population
  timeseries[year, 4] <- (1 - mortality_vector[4])*timeseries[year-1, 4] +
    growth_vector[3]*timeseries[year-1, 3]
  # Sum population for each year
  timeseries[year, 5] <- sum(timeseries[year, 1],
                             timeseries[year, 2],
                             timeseries[year, 3],
                             timeseries[year, 4])
}

# Adding years, since the time step is less than a year (3 months)
timeseries$year <- rep(1:Year, each = 4)
# Adding quarterly time step column
timeseries$quarter <- rep(paste0("Q", 1:4), Year)



### Plotting all populations to see what's happening

# Melt matrix to make plotting easier
tm_plot <- melt(timeseries[, -5], id.vars = c("year", "quarter"))
colnames(tm_plot)[3:4] <- c("size", "pop")


ggplot(tm_plot, aes(fill = quarter, y = pop, x = year)) +
  geom_bar(position="dodge", stat="identity") +
  facet_wrap(vars(size)) +
  theme_bw()




### Function to generate population for all size classes in next time step 
generate_fun <- function(t_minus_1,# The previous time step data (1 row, 4 columns for each size class)
                            growth, # growth rate vector for 3 smaller size classes
                            mortality, # mortality rate vector for all size classes
                            reproduction) { # reproductive rate vector for 3 larger size classes
  # Create vector to hold the current time step's population numbers
  t <- vector() 
  # Calculate small class population
  t[1] <- (1-(growth[1] + mortality[1]))*t_minus_1[, 1] + 
    reproduction[1]*t_minus_1[, 2] + 
    reproduction[2]*t_minus_1[, 3] +
    reproduction[3]*t_minus_1[, 4]
  # Calculate medium class population
  t[2] <- (1-(growth[2] + mortality[2]))*t_minus_1[, 2] +
    growth[1]*t_minus_1[, 1]
  # Calculate large class population
  t[3] <- (1-(growth[3] + mortality[3]))*t_minus_1[, 3] +
    growth[2]*t_minus_1[, 2]
  # Calculate x-large class population
  t[4] <- (1 - mortality[4])*t_minus_1[, 4] +
    growth[3]*t_minus_1[, 3]
  
  return(t)
}


```

### Second step: Removal

For the initial version of this, I'm assuming that removal is done using aerial dropped toxic baits, which can affect all size classes. I also assume that removals are done in the same time step length as the generating model (every 3 months), and that it occurs after natural births, growth and deaths in that time step.

Removal step for size class $i$ in time step $t$ is:

$$
n_{i,t} = (1-m_i)n_{i,t} 
$$

Where $m_i$ is the mortality rate from removal method for size class $i$.

What the code below is doing:

-   Create vector of $m_i$ values - initial values of all $m_i$ is 0.3

-   Create a dataframe for timeseries, with columns for each size class; the first row, time $t_1$, has 250 individuals in each size class

-   Loop from 2 - 80 time steps OR until condition met:

    -   Generate new population for time step, using function defined in generating_model chunk

    -   Using new population, perform removal step, using function defined in removals chunk

    -   If any size class populations go below 1, set population to 0

    -   Sum size class population into 5th column; if total population is less than or equal to 1, stop loop

```{r removals}

# Function to remove individuals 
removal_fun <- function(data, # one time step of data with all size classes, in vector form
                        size, # size class
                        m_rate) { # mortality rate for this size class from removal process
  new_data <- data[size]*(1 - m_rate)
  return(new_data)
}

# Size specific mortality rates from removal method
m_rate <- c("small" = 0.3,
            "medium" = 0.3,
            "large" = 0.3,
            "xlarge" = 0.3)

# Setting up new dataframe for timeseries with both generating and removals, starting with a larger population (N = 1000, still equally distributed across size classes)
timeseries_rm <- timeseries[0, 1:5]
timeseries_rm[1, ] <- c(rep(250, 4), 1000)


### Using a large loop with an if statement to break it once conditions are met (N <= 1)

for(ts in 2:(Year*4)) {
  # Generate next time step populations
  all_pop <- generate_fun(t_minus_1 = timeseries_rm[ts-1,],
                                       growth = growth_vector,
                                       mortality = mortality_vector,
                                       reproduction = repro_vector)
  # print(all_pop)
  # Perform removal
  remove_pop <- as.data.frame(matrix(NA, ncol = 4, nrow = 1))
  colnames(remove_pop) <- colnames(timeseries[,1:4])
  ind_removed <- vector()
  for(size in 1:length(bins)) {
  remove_pop[,size] <- removal_fun(all_pop, size, m_rate[size])
  # If any size classes have less than 1, convert to 0
  if((remove_pop[, size] < 1) == TRUE) {
    remove_pop[, size] <- 0 }
    else {
      remove_pop[, size] <- remove_pop[, size]
    }
  }

  timeseries_rm[ts, 1:4] <- remove_pop
  # Sum population after generation and removal steps
  timeseries_rm$total[ts] <- sum(remove_pop)
  if((timeseries_rm$total[ts] <= 1) == TRUE) {
    break
  }
}

# Adding year and quarter columns
timeseries_rm$year <- timeseries$year[1:nrow(timeseries_rm)]
timeseries_rm$quarter <- timeseries$quarter[1:nrow(timeseries_rm)]

timeseries_rm

### Plotting all populations to see what's happening

# Melt matrix to make plotting easier
tm_rm_plot <- melt(timeseries_rm[, -5], id.vars = c("year", "quarter"))
colnames(tm_rm_plot)[3:4] <- c("size", "pop")

ggplot(tm_rm_plot, aes(fill = quarter, y = pop, x = year)) +
  geom_bar(position="dodge", stat="identity") +
  facet_wrap(vars(size)) +
  theme_bw()

```

### Third step: Observation model

The assumptions for the observation model are based on the visual survey method, which have roughly the same detection probability across size classes (while traps miss small size class). Initially, detection probability $p = 1$ (perfect detection). Also, observation occurs every 4th time step (once per year).

```{r observation}

# Vector of detection probability for each size class
p_prob <- c("small" = 1,
            "medium" = 1,
            "large" = 1,
            "xlarge" = 1)

# Setting up new dataframe for timeseries with observed populations, taken every 4th time step
timeseries_obs <- timeseries[0, 1:5]

# Creating separate timeseries to store actual population, for every time step to have something to observe, starting with N = 10,000, still equally distributed across size classes
timeseries_raw <- timeseries[0, 1:5]
timeseries_raw[1, ] <- c(rep(2500, 4), 10000)

### Using a large loop with an if statement to break it once conditions are met (N <= 1)

for(ts in 2:(Year*4)) {
  # Generate next time step populations
  all_pop <- generate_fun(t_minus_1 = timeseries_raw[ts-1,],
                                       growth = growth_vector,
                                       mortality = mortality_vector,
                                       reproduction = repro_vector)
  # print(all_pop)
  # Perform removal
  remove_pop <- as.data.frame(matrix(NA, ncol = 4, nrow = 1))
  colnames(remove_pop) <- colnames(timeseries[,1:4])
  ind_removed <- vector()
  for(size in 1:length(bins)) {
  remove_pop[,size] <- removal_fun(all_pop, size, m_rate[size])
  # If any size classes have less than 1, convert to 0
  if((remove_pop[, size] < 1) == TRUE) {
    remove_pop[, size] <- 0 }
    else {
      remove_pop[, size] <- remove_pop[, size]
    }
  }
  
  timeseries_raw[ts, 1:4] <- remove_pop
  # Sum population after generation and removal steps
  timeseries_raw$total[ts] <- sum(remove_pop)
  
  # Observation step; every fourth time step, estimate population using p_prob
  if(ts%%4 == 0) {
    timeseries_obs[ts, 1:4] <- timeseries_raw[ts, 1:4]*p_prob
    timeseries_obs$total[ts] <-  timeseries_raw$total[ts]
  } else {
    timeseries_obs[ts, 1:4] <- rep(NA, 4)
  }
  
  # If total population goes below 1, stop loop
  if((timeseries_raw$total[ts] <= 1) == TRUE) {
    break
  }
}

# Adding year and quarter to both raw and observation timeseries
timeseries_raw$year <- timeseries$year[1:nrow(timeseries_raw)]
timeseries_raw$quarter <- timeseries$quarter[1:nrow(timeseries_raw)]
timeseries_obs$year <- timeseries_raw$year
timeseries_obs$quarter <- timeseries_raw$quarter

# Excluding time steps with no observation step from observation dataframe
timeseries_obs_only <- drop_na(timeseries_obs, "small")
timeseries_obs_only$year <- c(1:nrow(timeseries_obs_only))

### Plotting all populations to see what's happening
# Melt observationi dataframe to make plotting easier
tm_obs_plot <- melt(timeseries_obs[, -5], id.vars = c("year", "quarter"))
colnames(tm_obs_plot)[3:4] <- c("size", "pop")

### Plotting observations only
ggplot(tm_obs_plot, aes(fill = size, y = pop, x = year)) +
  geom_bar(position="dodge", stat="identity") +
  theme_bw() +
  labs(title = "Observation only", subtitle = "Sampled in Q4")


### Plotting both raw timeseries and observation
# Combine raw and observed dataframes, and melting to plot
timeseries_raw$data_type <- "raw"
timeseries_obs$data_type <- "observed"
tm_raw_obs_plot <- melt(rbind(timeseries_raw[, -5], timeseries_obs[, -5]), id.vars = c("year", "data_type", "quarter"))
colnames(tm_raw_obs_plot)[4:5] <- c("size", "pop")
tm_raw_obs_plot <- drop_na(tm_raw_obs_plot, "pop")


# Plot
ggplot(tm_raw_obs_plot, aes(fill = quarter, y = pop, x = year)) +
  geom_bar(position="dodge", stat="identity") +
  facet_grid(data_type ~ size) +
  theme_bw()





```
