---
title: "HMU Experiment Comparison"
author: "Kelly Mistry"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(reshape2)
library(ggplot2)
library(dplyr)
library(here)
library(tictoc)
library(fdrtool)
library(jagsUI)
library(scales)
library(vctrs)
library(stringr)
library(readxl)

source(here("Scripts/00_user_inputs.R"))
source(here("Scripts/01_model_functions.R"))
source(here("Scripts/02_results_functions.R"))
source(here("Scripts/model_evaluation.R"))

## Setting up plot colors to standardize across plots
# Size class colors
plot_colors <- list()
plot_colors$size_class <- c(hue_pal()(4), "black")
names(plot_colors$size_class) <- c(size_class_names, "unknown")
```

# Comparing HMU experimental data to IBM simulation results

The HMU is 55 ha, in a roughly rectangular shape, with a maximum width of 480 m (according to statement of work). There are 65 planned transects across the entire area, spaced 20 m apart, but they only ended up using 13 transects over \~ 4 months due to Typhoon Mawar. Traps and bait tubes were alternated, spaced 20 m apart from each other on the transect (trap - 10 m - tube - 10 m - trap - 10 m - tube, etc.).

They used a rolling wave of treatments, with 6 weeks of traps and bait tubes sequentially on each transect, with visual surveys occurring on the 1st, 6th and 11th weeks.

```{r import_HMU_data}

### Import HMU data
# Trap effort data
HMU_trap_data <- read_xlsx(here("Data", "HMU", "HMU_USDA_trap_data.xlsx"), sheet = "Trap Checks")
# Trap snake capture data
HMU_trap_capture_data <- read_xlsx(here("Data", "HMU", "HMU_USDA_trap_data.xlsx"), sheet = "Trap Captures")
# Bait tube effort data
HMU_bait_tube_data <- read_xlsx(here("Data", "HMU", "HMU_USDA_trap_data.xlsx"), sheet = "Tube Checks")
# Visual survey effort & snake capture data
HMU_vis_data <- read.csv(here("Data", "HMU", "HMU_USGS_VIS_survey_data.csv"))


num_weeks <- length(unique(HMU_trap_data$setdate))
# 16 weeks of data available; 1 quarter + 3 weeks

# Converting the effort dates into numbered days, with the first ADS drop (1/30/23) acting as the first day of the first quarter

HMU_trap_data$lastcheck <- as.Date(HMU_trap_data$lastcheck)
trap_days <- vector()
trap_days[1] <- 11
for(i in 1:(length(unique(HMU_trap_data$lastcheck))-1)) {
  trap_days[i+1] <- trap_days[i] + as.integer(unique(HMU_trap_data$lastcheck)[i+1] - unique(HMU_trap_data$lastcheck)[i])
}

HMU_bait_tube_data$checkdate <- as.Date(HMU_bait_tube_data$checkdate)
bait_tube_days <- vector()
bait_tube_days[1] <- trap_days[2]
for(i in 1:(length(unique(HMU_bait_tube_data$checkdate))-1)) {
  bait_tube_days[i+1] <- bait_tube_days[i] + as.integer(unique(HMU_bait_tube_data$checkdate)[i+1] - unique(HMU_bait_tube_data$checkdate)[i])
}

HMU_vis_data$effortdate <- as.Date(HMU_vis_data$effortdate)
vis_days <- vector()
vis_days[1] <- 8
for(i in 1:(length(unique(HMU_vis_data$effortdate))-1)){
  vis_days[i+1] <- vis_days[i] + as.integer(unique(HMU_vis_data$effortdate)[i+1] - unique(HMU_vis_data$effortdate)[i])
}

## ADS drops were done on: 1/30/23, 2/3/23, 5/1/23, 5/4/23
ADS_dates <- as.Date(c("01/30/23", "02/03/23", "05/01/23", "05/04/23"), format = "%m/%d/%y")
ADS_days <- vector()
ADS_days[1] <- 1
for(i in 1:(length(ADS_dates)-1)){
  ADS_days[i+1] <- ADS_days[i] + as.integer(ADS_dates[i+1] - ADS_dates[i])
}

method_days <- list("ADS" = ADS_days,
                    "visual" = vis_days,
                    "trap" = trap_days,
                    "bait_tube" = bait_tube_days)

### Reformatting trap captured snake data 
# Remove all NA row (not sure why its there)
HMU_trap_capture_data <- HMU_trap_capture_data[-which(is.na(HMU_trap_capture_data$uid)),]
# Splitting out capture IDs into its components (capture date, transect, trap, and the number of snakes found in the trap)
HMU_trap_capture_data[c("capture_date", "transect", "trap", "snake_num")] <- str_split_fixed(HMU_trap_capture_data$uid, "-", 4)
HMU_trap_capture_data$capture_date <- as.Date(HMU_trap_capture_data$capture_date, format = "%Y%m%d")
# Numbering days relative to 2/6/23 (day 1)
HMU_trap_capture_data$numbered_day <- 0
HMU_trap_capture_data$numbered_day[1] <- 4
for(i in 2:nrow(HMU_trap_capture_data)) {
  HMU_trap_capture_data$numbered_day[i] <- HMU_trap_capture_data$numbered_day[i-1] + as.integer(HMU_trap_capture_data$capture_date[i] - HMU_trap_capture_data$capture_date[i-1])
}
# Adding size class
HMU_trap_capture_data$`svl (mm)` <- as.numeric(HMU_trap_capture_data$`svl (mm)`)
HMU_trap_capture_data$size_class <- NA
for(i in 1:nrow(HMU_trap_capture_data)) {
  if(is.na(HMU_trap_capture_data$`svl (mm)`[i]) != TRUE) {
    HMU_trap_capture_data$size_class[i] <- size_class_fun(HMU_trap_capture_data$`svl (mm)`[i])
  } else {
    HMU_trap_capture_data$size_class[i] <- "unknown"
  }
}
HMU_trap_capture_data$size_class <- factor(HMU_trap_capture_data$size_class, levels = c(size_class_names, "unknown"))
# Adding quarter 
HMU_trap_capture_data$Quarter <- 0
for(i in 1:nrow(HMU_trap_capture_data)) {
  if(HMU_trap_capture_data$numbered_day[i] <= 91) {
    HMU_trap_capture_data$Quarter[i] <- 1
  } else {
    HMU_trap_capture_data$Quarter[i] <- 2
  }
}

# Separating out visual captured data and adding columns for numbered days (with 2/6/23 as day 1), size class, and quarter
HMU_vis_capture_data <- HMU_vis_data[HMU_vis_data$bts != 0,]
# Numbering days relative to 2/6/23 (day 1)
HMU_vis_capture_data$numbered_day <- 0
HMU_vis_capture_data$numbered_day[1] <- 1
for(i in 2:nrow(HMU_vis_capture_data)) {
  HMU_vis_capture_data$numbered_day[i] <- HMU_vis_capture_data$numbered_day[i-1] + as.integer(HMU_vis_capture_data$effortdate[i] - HMU_vis_capture_data$effortdate[i-1])
}
# Adding size class
HMU_vis_capture_data$size_class <- NA
for(i in 1:nrow(HMU_vis_capture_data)) {
  HMU_vis_capture_data$size_class[i] <- size_class_fun(HMU_vis_capture_data$svl[i])
}
HMU_vis_capture_data$size_class <- factor(HMU_vis_capture_data$size_class, levels = c(size_class_names, "unknown"))
# Adding quarter 
HMU_vis_capture_data$Quarter <- 0
for(i in 1:nrow(HMU_vis_capture_data)) {
  if(HMU_vis_capture_data$numbered_day[i] <= 91) {
    HMU_vis_capture_data$Quarter[i] <- 1
  } else {
    HMU_vis_capture_data$Quarter[i] <- 2
  }
}

# Combining vis and trap capture data with numbered day, size class, and quarter to compare to IBM via plotting 
# Adding method column to both dataframes in order to distinguish them
HMU_vis_capture_data$method <- "visual"
HMU_trap_capture_data$method <- "trap"
all_HMU_observed <- HMU_vis_capture_data[c("numbered_day", "size_class", "Quarter", "method")]
all_HMU_observed <- bind_rows(all_HMU_observed, HMU_trap_capture_data[c("numbered_day", "size_class", "Quarter", "method")])

# Plotting all observed for the first quarter
all_HMU_captures_plot <- ggplot(all_HMU_observed[all_HMU_observed$numbered_day <= 91,]) +
  geom_bar(aes(fill = size_class, x = as.character(Quarter)), position = "dodge", stat = "count") +
  scale_fill_manual(values = plot_colors$size_class) +
  facet_wrap(vars(method)) +
  theme_bw()


```

```{r simulation_model}

# Parameters that may be changed or subject to sensitivity analysis or to simulate over

# Set study/eradication area size (in ha), which dictates both K and the initial population
area_size <- 55

# Set carrying capacity for this population:
K <- 60*area_size

## For initial population, based on previous runs to find roughly eqiulibrium N and size distribution:
N <- 50*area_size
size_dist <- c(0.4, 0.1, 0.1, 0.4)

# Growth probability (p_g)
g_density_prob <- 0.75 

# Number of quarters to generate - 1 year
erad_quarter_time_step <- 2
day_time_step <- 91

# #### Original way to do quarters and days (same days in every quarter)
# # Quarters where eradication methods are used, and which days in that quarter:
# erad_quarters <- list()
# # erad_quarters$ADS <- # ask Shane and Amy when ADS occurred (it wasn't part of their experimental design, but it may have occurred)
# erad_quarters$visual <- c(1) # start with just the first 13 weeks
# erad_quarters$trap <- c(1)
# erad_quarters$bait_tube <- c(1)
# erad_days <- list()
# # erad_days$ADS <- 
# erad_days$visual <- vis_days[vis_days <= day_time_step]
# erad_days$trap <- trap_days[trap_days <= day_time_step]
# erad_days$bait_tube <- bait_tube_days[bait_tube_days <= day_time_step]

#### Trying out having quarter-specific days
erad_quarters <- list()
erad_quarters$ADS <- c(1,2)
erad_quarters$visual <- c(1,2)
erad_quarters$trap <- c(1,2)
erad_quarters$bait_tube <- c(1,2)
erad_days <- list()
erad_days$quarter_1 <- list()
erad_days$quarter_2 <- list()
for(method in erad_methods){
  erad_days[[1]][[method]] <- method_days[[method]][method_days[[method]] <= day_time_step]
  erad_days[[2]][[method]] <- method_days[[method]][method_days[[method]] > day_time_step] - day_time_step
}



# Number of teams for each of the transet-based methods
num_teams <- list()
num_teams$visual <- 1
num_teams$trap <- 1
num_teams$bait_tube <- 1

# Coverage for each method in a quarter 
num_transects <- 65
erad_coverage <- list()
erad_coverage$ADS <- 1 # for now, this stays in because daily_operations requires it - at some point fix this so it doesn't have to occur

# Coverage for all transect methods
erad_coverage$transects_per_quarter <- 15/num_transects
# Daily coverage amounts for each transect-based method (number of transects that can be covered by day by one team)
erad_coverage$visual <- 4
erad_coverage$trap <- 6
erad_coverage$bait_tube <- erad_coverage$trap*2

# Overlap of ADS over transects
ADS_overlap_on_transect <- 1 # i.e. total area coverage, by at least one method 


```

```{r run_IBM_once}

# Running model 
erad_quarter_results <- quarter_operations(initial_N = N, 
                                           initial_size_dist = size_dist, 
                                           p_g = g_density_prob,
                                           lambda = lambda,
                                           total_quarters = erad_quarter_time_step,
                                           total_days = day_time_step,
                                           erad = "on",
                                           erad_method = erad_methods,
                                           erad_coverage,
                                           primary_sampling_period = c(0,0),
                                           erad_quarters = erad_quarters,
                                           erad_days = erad_days)

# Plotting the total population in each quarter
erad_plot_1 <- ggplot(erad_quarter_results$all_quarters, 
                      aes(x = Quarter, fill = size_category)) +
  geom_bar() +
  geom_hline(yintercept = K) +
  theme_bw() +
  scale_x_continuous(breaks = unique(erad_quarter_results$all_quarters$Quarter), labels = unique(erad_quarter_results$all_quarters$Quarter))

# Plotting observed removed snakes (captured through trapping and visual survey)
observed_list <- erad_quarter_results$all_observed[unlist(lapply(erad_quarter_results$all_observed, length) != 0)]
all_observed <- bind_rows(observed_list)
for(snake in 1:nrow(all_observed)){
  all_observed$size_category[snake] <- size_class_fun(all_observed$SVL[snake], 
                                                      size_class_limits)
}
# Factoring size category column for graphing
all_observed$size_category <- factor(all_observed$size_category, 
                                     levels = c("small", "medium", "large", "xlarge"))

# Scatter plot, SVL size on the y-axis, separated by quarter
observed_plot_1 <- ggplot(all_observed, aes(x = day, y = SVL, color = method)) +
  geom_jitter() +
  theme_bw() +
  facet_wrap("quarter")
# Bar plot
observed_plot_2 <- ggplot(all_observed, aes(fill = size_category, x = as.character(quarter))) +
  geom_bar(position = "dodge") +
  facet_wrap("method") +
  theme_bw()

# Plotting unobserved removed snakes (killed through ADS and bait tubes)
unobserved_list <- erad_quarter_results$all_unobserved[unlist(lapply(erad_quarter_results$all_unobserved, length) != 0)]
all_unobserved <- bind_rows(unobserved_list[c(1:3)])
for(snake in 1:nrow(all_unobserved)){
  all_unobserved$size_category[snake] <- size_class_fun(all_unobserved$SVL[snake], 
                                                      size_class_limits)
}
# Factoring size category column for graphing
all_unobserved$size_category <- factor(all_unobserved$size_category, 
                                     levels = c("small", "medium", "large", "xlarge"))

unobserved_plot_1 <- ggplot(all_unobserved , aes(x = day, y = SVL, color = method)) +
  geom_jitter() +
  theme_bw() +
  facet_wrap("quarter")
unobserved_plot_2 <- ggplot(all_unobserved, aes(fill = size_category, x = as.character(quarter))) +
  geom_bar(position = "dodge") +
  facet_wrap("method") +
  theme_bw()
```

There were a total of 36 snakes captured in traps and 14 captured during visual surveys. The first run of the model returned 42 trap captures and 24 from visual survey, which is not incredibly far off. Run 100 and look at the mean and range of values, as well as the size class distribution of captures by each method.

```{r IBM_size_dist_variants}

# Number of replicates
num_replicates <- 100

# Size distribution variants
size_dist_variants <- list()
size_dist_variants[[1]] <- c(0.4, 0.1, 0.1, 0.4) # default - stable size dist in IBM at K
size_dist_variants[[2]] <- c(1/4, 1/4, 1/4, 1/4) # equal distribution

size_dist_variants[[3]] <- c(3/8, 2/8, 2/8, 1/8) # More small, less x-large
size_dist_variants[[4]] <- c(3/8, 1/8, 2/8, 2/8) # More small, less medium
size_dist_variants[[5]] <- c(3/8, 2/8, 1/8, 2/8) # More small, less large

size_dist_variants[[6]] <- c(1/8, 3/8, 2/8, 2/8) # More medium, less small
size_dist_variants[[7]] <- c(2/8, 3/8, 1/8, 2/8) # More medium, less large
size_dist_variants[[8]] <- c(2/8, 3/8, 2/8, 1/8) # More medium, less x-large

size_dist_variants[[9]] <- c(1/8, 2/8, 3/8, 2/8) # More large, less small
size_dist_variants[[10]] <- c(2/8, 1/8, 3/8, 2/8) # More large, less medium
size_dist_variants[[11]] <- c(2/8, 2/8, 3/8, 1/8) # More large, less x-large

size_dist_variants[[12]] <- c(1/8, 2/8, 2/8, 3/8) # Mor x-large, less small
size_dist_variants[[13]] <- c(2/8, 1/8, 2/8, 3/8) # Mor x-large, less medium
size_dist_variants[[14]] <- c(2/8, 2/8, 1/8, 3/8) # Mor x-large, less large


### Iterating over each size distribution * number of replicates (1,400 total replicates)
# Using all of the parameters from single run above, except for size_dist which I'm replacing with each variant

size_var_IBM_results <- list()
for(size_var in 4:length(size_dist_variants)) {
  size_dist <- size_dist_variants[[size_var]] 
  size_var_IBM_results[[size_var]] <- list()
  for(n in 1:num_replicates) {
    # Running model 
   size_var_IBM_results[[size_var]][[n]] <- quarter_operations(initial_N = N, 
                                             initial_size_dist = size_dist, 
                                             p_g = g_density_prob,
                                             lambda = lambda,
                                             total_quarters = erad_quarter_time_step,
                                             total_days = day_time_step,
                                             erad = "on",
                                             erad_method = erad_methods,
                                             erad_coverage,
                                             primary_sampling_period = c(0,0),
                                             erad_quarters = erad_quarters,
                                             erad_days = erad_days)
   print(paste0("replicate ", n, " complete"))
  }
  # Save each variant list
  saveRDS(size_var_IBM_results[[size_var]], file = here("Results", "HMU", paste0("ADS_included_var_", size_var, ".rds")))
  print(paste0("size dist variant ", size_var, " complete"))
}


```

```{r IBM_results_wout_ADS}

# IBM_results_list <- readRDS(file = here("Results", "HMU", paste0("size_dist_var_", 1, ".rds")))

size_var_all_observed <- list()
for(var in 1:length(size_dist_variants)) {
  # Read in IBM results
  size_var_IBM_results <- readRDS(file = here("Results", "HMU", paste0("size_dist_var_", var, ".rds")))
  # List to store observed snakes
  all_observed_list <- list()
  for(rep in 1:num_replicates) {
    # Separate out results from one replicate, and combined observations from all quarters where observation methods occurred
   rep_observed <- size_var_IBM_results[[rep]]$all_observed[unlist(lapply(size_var_IBM_results[[rep]]$all_observed, length) != 0)]
   # Drop any empty dataframes (where no snakes were captured)
   rep_observed <- list_drop_empty(rep_observed)
   observed_list <- bind_rows(rep_observed)
   # Adding size class column
    for(snake in 1:nrow(observed_list)){
      observed_list$size_category[snake] <- size_class_fun(observed_list$SVL[snake], size_class_limits)
    }
    # Factoring size category column for graphing
    observed_list$size_category <- factor(observed_list$size_category, 
                                         levels = c("small", "medium", "large", "xlarge"))
    # Constructing list of lists to contain dataframes with the number of snakes observed through each method in each size class in each quarter
    all_observed_list[[rep]] <- list()
    observed_methods <- unique(observed_list$method)
    for(method in 1:length(observed_methods)) {
      all_observed_list[[rep]][[method]] <- list()
      for(quarter in unique(observed_list$quarter)) {
        all_observed_list[[rep]][[method]][[quarter]] <- as.data.frame(matrix(NA, nrow = 4, ncol = 2)) 
        colnames(all_observed_list[[rep]][[method]][[quarter]]) <- c("size_class", "removed")
        all_observed_list[[rep]][[method]][[quarter]]$size_class <- size_class_names
        for(size in 1:length(size_class_names)) {
          all_observed_list[[rep]][[method]][[quarter]]$removed[size] <- nrow(observed_list[observed_list$size_category == size_class_names[size] & observed_list$method == observed_methods[method] & observed_list$quarter == quarter, ])
        }
      }
    }
      names(all_observed_list[[rep]]) <- observed_methods
  }
  # Melting the list of lists to create a single dataframe 
  all_observed <- melt(all_observed_list, id.vars = colnames(all_observed_list[[1]][[1]][[1]]))
  colnames(all_observed)[c(3:5)] <- c("quarter", "method", "rep")
  # Labeling replicates
  all_observed$rep <- paste0("replicate_", all_observed$rep)
  all_observed$source <- "simulated"
  all_observed$size_class <- factor(all_observed$size_class, levels = size_class_names)
  # Saving final dataframe
  size_var_all_observed[[var]] <- all_observed
}
# Naming each size distribution variation list element
names(size_var_all_observed) <- paste0("size_dist_variants_", c(1:length(size_dist_variants))) # Melting into one dataframe for plotting
melted_size_var_observed <- melt(size_var_all_observed, id.vars = colnames(size_var_all_observed[[1]]))
colnames(melted_size_var_observed)[7] <- "variant"

# Reformatting HMU data to plot with the IBM results
HMU_observed <- list()
for(method in 1:length(observed_methods)) {
   HMU_observed[[method]] <- list()
  for(quarter in c(1:2)) {
    HMU_observed[[method]][[quarter]] <- as.data.frame(matrix(NA, nrow = 4, ncol = 2))
    colnames(HMU_observed[[method]][[quarter]]) <- c("size_class", "removed")
    HMU_observed[[method]][[quarter]]$size_class <- size_class_names
    for(size in 1:length(size_class_names)) {
      HMU_observed[[method]][[quarter]]$removed[size] <- nrow(all_HMU_observed[all_HMU_observed$Quarter == quarter & all_HMU_observed$size_class == size_class_names[size] & all_HMU_observed$method == observed_methods[method],])
    }
  }
}
names(HMU_observed) <- observed_methods

all_HMU_summed <- melt(HMU_observed, id.vars = colnames(HMU_observed[[1]][[1]]))
colnames(all_HMU_summed)[c(3:4)] <- c("quarter", "method")
all_HMU_summed$source <- "HMU_data"

# Bar plot
observed_plot <- ggplot() +
  geom_violin(data = melted_size_var_observed, aes(fill = variant, y = removed, x = size_class)) +
  geom_point(data = all_HMU_summed[all_HMU_summed$quarter == 1,], aes(y = removed, x = size_class), size = 2, color = "black") +
  facet_wrap(vars(method)) +
  theme_bw() +
  guides(fill = "none") +
  labs(y = "Removed individuals", x = "Size class")
 
 
 
  
  
  
```

```{r IBM_results_w_ADS}

results_names <- c("fewest_small", "fewest_xlarge", "most_large", "stable_dist", "uniform")

size_var_all_observed <- list()
for(var in 1:length(results_names)) {
  # Read in IBM results
  size_var_IBM_results <- readRDS(file = here("Results", "HMU", paste0("ADS_included_", results_names[var], ".rds")))
  # List to store observed snakes
  all_observed_list <- list()
  for(rep in 1:num_replicates) {
    # Separate out results from one replicate, and combined observations from all quarters where observation methods occurred
   rep_observed <- size_var_IBM_results[[rep]]$all_observed[unlist(lapply(size_var_IBM_results[[rep]]$all_observed, length) != 0)]
   # Drop any empty dataframes (where no snakes were captured)
   rep_observed <- list_drop_empty(rep_observed)
   observed_list <- bind_rows(rep_observed)
   # Adding size class column
    for(snake in 1:nrow(observed_list)){
      observed_list$size_category[snake] <- size_class_fun(observed_list$SVL[snake], size_class_limits)
    }
    # Factoring size category column for graphing
    observed_list$size_category <- factor(observed_list$size_category, 
                                         levels = c("small", "medium", "large", "xlarge"))
    # Constructing list of lists to contain dataframes with the number of snakes observed through each method in each size class in each quarter
    all_observed_list[[rep]] <- list()
    observed_methods <- unique(observed_list$method)
    for(method in 1:length(observed_methods)) {
      all_observed_list[[rep]][[method]] <- list()
      for(quarter in unique(observed_list$quarter)) {
        all_observed_list[[rep]][[method]][[quarter]] <- as.data.frame(matrix(NA, nrow = 4, ncol = 2)) 
        colnames(all_observed_list[[rep]][[method]][[quarter]]) <- c("size_class", "removed")
        all_observed_list[[rep]][[method]][[quarter]]$size_class <- size_class_names
        for(size in 1:length(size_class_names)) {
          all_observed_list[[rep]][[method]][[quarter]]$removed[size] <- nrow(observed_list[observed_list$size_category == size_class_names[size] & observed_list$method == observed_methods[method] & observed_list$quarter == quarter, ])
        }
      }
    }
      names(all_observed_list[[rep]]) <- observed_methods
  }
  # Melting the list of lists to create a single dataframe 
  all_observed <- melt(all_observed_list, id.vars = colnames(all_observed_list[[1]][[1]][[1]]))
  colnames(all_observed)[c(3:5)] <- c("quarter", "method", "rep")
  # Labeling replicates
  all_observed$rep <- paste0("replicate_", all_observed$rep)
  all_observed$source <- "simulated"
  all_observed$size_class <- factor(all_observed$size_class, levels = size_class_names)
  # Saving final dataframe
  size_var_all_observed[[var]] <- all_observed
}
# Naming each size distribution variation list element
names(size_var_all_observed) <- paste0(results_names) # Melting into one dataframe for plotting
melted_size_var_observed <- melt(size_var_all_observed, id.vars = colnames(size_var_all_observed[[1]]))
colnames(melted_size_var_observed)[7] <- "variant"


# Reformatting HMU data to plot with the IBM results
HMU_observed <- list()
for(method in 1:length(observed_methods)) {
   HMU_observed[[method]] <- list()
  for(quarter in c(1:2)) {
    HMU_observed[[method]][[quarter]] <- as.data.frame(matrix(NA, nrow = 4, ncol = 2))
    colnames(HMU_observed[[method]][[quarter]]) <- c("size_class", "removed")
    HMU_observed[[method]][[quarter]]$size_class <- size_class_names
    for(size in 1:length(size_class_names)) {
      HMU_observed[[method]][[quarter]]$removed[size] <- nrow(all_HMU_observed[all_HMU_observed$Quarter == quarter & all_HMU_observed$size_class == size_class_names[size] & all_HMU_observed$method == observed_methods[method],])
    }
  }
}
names(HMU_observed) <- observed_methods

all_HMU_summed <- melt(HMU_observed, id.vars = colnames(HMU_observed[[1]][[1]]))
colnames(all_HMU_summed)[c(3:4)] <- c("quarter", "method")
all_HMU_summed$source <- "HMU_data"

# Bar plot
observed_plot <- ggplot() +
  geom_violin(data = melted_size_var_observed, aes(fill = variant, y = removed, x = size_class)) +
  geom_point(data = all_HMU_summed, aes(y = removed, x = size_class), size = 2, color = "black") +
  facet_wrap(vars(method, quarter)) +
  theme_bw() +
  #guides(fill = "none") +
  labs(y = "Removed individuals", x = "Size class")
```
